

    \filetitle{barcon}{Contribution bar graph for tseries objects}{tseries/barcon}

	\paragraph{Syntax}

\begin{verbatim}
[H,Range] = barcon(X,...)
[H,Range] = barcon(Range,X,...)
[H,Range] = barcon(Ax,Range,X,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{Ax} {[} handle \textbar{} numeric {]} - Handle to axes in
  which the graph will be plotted; if not specified, the current axes
  will used.
\item
  \texttt{Range} {[} numeric {]} - Date range; if not specified the
  entire range of the input tseries object will be plotted.
\item
  \texttt{X} {[} tseries {]} - Input tseries object whose columns will
  be ploted as a contribution bar graph.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{H} {[} handle \textbar{} numeric {]} - Handles to the bars
  plotted.
\item
  \texttt{Range} {[} numeric {]} - Actually plotted date range.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'barWidth='} {[} numeric \textbar{} \emph{\texttt{0.8}} {]} -
  Width of bars as a percentage of the space each period occupies on the
  x-axis.
\item
  \texttt{'colorMap='} {[} numeric \textbar{}
  \emph{\texttt{get(gcf(),'colorMap')}} {]} - Color map used to fill the
  contribution bars.
\item
  \texttt{'evenlySpread='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Colors picked for the contribution bars are
  evenly spread across the color map.
\item
  \texttt{'ordering='} {[} \texttt{'ascend'} \textbar{}
  \texttt{'descend'} \textbar{} \emph{\texttt{'preserve'}} \textbar{}
  numeric {]} - Ordering of contributions with the same sign withinin
  each period; \texttt{'preserve'} means the original order will be
  preserved.
\end{itemize}

See help on \href{tseries/plot}{\texttt{tseries/plot}} and the built-in
function \texttt{bar} for other options available.

\paragraph{Description}

\paragraph{Example}


