

    \filetitle{bpass}{Band-pass filter}{tseries/bpass}

	\paragraph{Syntax}

\begin{verbatim}
[X,T] = bpass(X,Band,Range,...)
\end{verbatim}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{X} {[} tseries {]} - Band-pass filtered tseries object.
\item
  \texttt{T} {[} tseries {]} - Estimated trend tseries object.
\end{itemize}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{X} {[} tseries {]} - Input tseries object that will be
  filtered.
\item
  \texttt{Range} {[} numeric \textbar{} Inf {]} Date range on which the
  data will be filtered.
\item
  \texttt{Band} {[} numeric {]} - Band of periodicities to be retained
  in the output data, \texttt{Band = {[}LOW,HIGH{]}}.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'addTrend='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Add the estimated linear time trend back to
  filtered output series if \texttt{band} includes Inf.
\item
  \texttt{'detrend='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Remove an estimated time trend from the data before filtering.
\item
  \texttt{'log='} {[} \texttt{true} \textbar{} \emph{\texttt{false}} {]}
  - Logarithmise the data before filtering, de-logarithmise afterwards.
\item
  \texttt{'method='} {[} \emph{\texttt{'cf'}} \textbar{}
  \texttt{'hwfsf'} {]} - Type of band-pass filter:
  Christiano-Fitzgerald, or h-windowed frequency-selective filter.
\item
  \texttt{'unitRoot='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Assume unit root in the input data.
\end{itemize}

See help on \href{tseries/trend}{\texttt{tseries/trend}} for other
options available when \texttt{'detrend='} is set to true.

\paragraph{Description}

Christiano, L.J. and T.J.Fitzgerald (2003). The Band Pass Filter.
International Economic Review, 44(2), 435--465.

Iacobucci, A. \& A. Noullez (2005). A Frequency Selective Filter for
Short-Length Time Series. Computational Economics, 25, 75--102.

\paragraph{Example}


