

    \filetitle{bwf}{Butterworth filter with tunes}{tseries/bwf}

	\paragraph{Syntax}

\begin{verbatim}
[T,C,CutOff,Lambda] = bwf(X,Order)
[T,C,CutOff,Lambda] = bwf(X,Order,Range,...)
\end{verbatim}

\paragraph{Syntax with output arguments
swapped}

\begin{verbatim}
[T,C,CutOff,Lambda] = bwf2(X,Order)
[T,C,CutOff,Lambda] = bwf2(X,Order,Range,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{X} {[} tseries {]} - Input tseries object that will be
  filtered.
\item
  \texttt{Order} {[} numeric {]} - Order of the Butterworth filter; note
  that \texttt{Order=2} reproduces the Hodrick-Prescott filter
  (\texttt{hpf}) and \texttt{Order=1} reproduces the local linear filter
  (\texttt{llf}).
\item
  \texttt{Range} {[} numeric {]} - Date Range on which the input data
  will be filtered; \texttt{Range} can be \texttt{Inf},
  \texttt{{[}startdata,Inf{]}}, or \texttt{{[}-Inf,enddate{]}}; if not
  specifired, \texttt{Inf} (i.e.~the entire available Range of the input
  series) is used.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{T} {[} tseries {]} - Lower-frequency (trend) component.
\item
  \texttt{C} {[} tseries {]} - Higher-frequency (cyclical) component.
\item
  \texttt{CutOff} {[} numeric {]} - Cut-off periodicity; periodicities
  above the cut-off are attributed to trends, periodicities below the
  cut-off are attributed to gaps.
\item
  \texttt{Lambda} {[} numeric {]} - Smoothing parameter actually used;
  this output argument is useful when the option \texttt{'CutOff='} is
  used instead of \texttt{'Lambda='}.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'CutOff='} {[} numeric \textbar{} \emph{empty} {]} - Cut-off
  periodicity in periods (depending on the time series frequency); this
  option can be specified instead of \texttt{'Lambda='}; the smoothing
  parameter will be then determined based on the cut-off periodicity.
\item
  \texttt{'CutOffYear='} {[} numeric \textbar{} \emph{empty} {]} -
  Cut-off periodicity in years; this option can be specified instead of
  \texttt{'Lambda='}; the smoothing parameter will be then determined
  based on the cut-off periodicity.
\end{itemize}

\texttt{'infoSet='} {[} \texttt{1} \textbar{} \emph{\texttt{2}} {]} -
Information set assumption used in the filter: \texttt{1} runs a
one-sided filter, \texttt{2} runs a two-sided filter.

\begin{itemize}
\item
  \texttt{'Lambda='} {[} numeric \textbar{} \emph{\texttt{@auto}} {]} -
  Smoothing parameter; needs to be specified for tseries objects with
  indeterminate frequency. See Description for default values.
\item
  \texttt{'level='} {[} tseries {]} - Time series with soft and hard
  tunes on the level of the trend.
\item
  \texttt{'change='} {[} tseries {]} - Time series with soft and hard
  tunes on the change in the trend.
\item
  \texttt{'log='} {[} \texttt{true} \textbar{} \emph{\texttt{false}} {]}
  - Logarithmise the data before filtering, de-logarithmise afterwards.
\end{itemize}

\paragraph{Description}

\subparagraph{Default smoothing
parameters}

If the user does not specify the smoothing parameter using the
\texttt{'lambda='} option (or reassigns the default \texttt{@auto}), a
default value is used. The default value is based on common practice and
can be calculated using the date frequency of the input time series as
$\lambda = (10 \cdot f)^n$, where $f$ is the frequency (yearly=1,
half-yearly=2, quarterly=4, bi-monthly=6, monthly=12), and $n$ is the
order of the filter, determined by the input parameter \texttt{Order}.

\paragraph{Example}


