
    \foldertitle{tseries}{Time Series (tseries Objects)}{tseries/Contents}

	tseries methods:

\paragraph{Constructor}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{tseries/tseries}{\texttt{tseries}} - Create new time series
  (tseries) object.
\end{itemize}

\paragraph{Getting information about tseries
objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{tseries/enddate}{\texttt{enddate}} - Date of the last available
  observation in a tseries object.
\item
  \href{tseries/freq}{\texttt{freq}} - Date frequency of tseries object.
\item
  \href{tseries/get}{\texttt{get}} - Query tseries object property.
\item
  \href{tseries/isequal}{\texttt{isequal}} - {[}Not a public function{]}
  Compare two tseries objects.
\item
  \href{tseries/length}{\texttt{length}} - Length of tseries object.
\item
  \href{tseries/ndims}{\texttt{ndims}} - Number of dimensions in tseries
  object data.
\item
  \href{tseries/size}{\texttt{size}} - Size of tseries object data.
\item
  \href{tseries/startdate}{\texttt{startdate}} - Date of the first
  available observation in a tseries object.
\item
  \href{tseries/yearly}{\texttt{yearly}} - Display tseries object one
  calendar year per row.
\end{itemize}

\paragraph{Referencing tseries
objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{tseries/subsasgn}{\texttt{subsasgn}} - Subscripted assignment
  for tseries objects.
\item
  \href{tseries/subsref}{\texttt{subsref}} - Subscripted reference
  function for tseries objects.
\end{itemize}

\paragraph{Maths and statistics functions and
operators}

Some of the following functions require the Statistics Toolbox.

\texttt{+}, \texttt{-}, \texttt{*}, \texttt{\textbackslash{}},
\texttt{/}, \texttt{\^{}}, \texttt{\&}, \texttt{\textbar{}},
\texttt{\textasciitilde{}}, \texttt{==}, \texttt{\textasciitilde{}=},
\texttt{\textgreater{}=}, \texttt{\textgreater{}}, \texttt{\textless{}},
\texttt{\textless{}=}, \texttt{abs}, \texttt{acos}, \texttt{asin},
\texttt{atan}, \texttt{atan2}, \texttt{ceil}, \texttt{cos},
\texttt{exp}, \texttt{fix}, \texttt{floor},\texttt{imag},
\texttt{isinf}, \texttt{isnan}, \texttt{log}, \texttt{log10},
\texttt{real}, \texttt{round}, \texttt{sin}, \texttt{sqrt},
\texttt{tan}, \texttt{normpdf}, \texttt{normcdf}, \texttt{prctile},
\texttt{lognpdf}, \texttt{logncdf}

The behaviour of the following functions depend on the dimension along
which they are performed.

Some of the following functions require the Statistics Toolbox.

\texttt{all}, \texttt{any}, \texttt{cumprod}, \texttt{cumsum},
\texttt{find}, \texttt{geomean}, \texttt{max}, \texttt{mean},
\texttt{median}, \texttt{min}, \texttt{mode}, \texttt{nanmean},
\texttt{nanstd}, \texttt{nansum}, \texttt{nanvar}, \texttt{prod},
\texttt{std}, \texttt{sum}, \texttt{var}

\paragraph{Filters and evaluation}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{tseries/arf}{\texttt{arf}} - Run autoregressive function on a
  tseries object.
\item
  \href{tseries/arma}{\texttt{arma}} - Apply ARMA model to input series.
\item
  \href{tseries/bpass}{\texttt{bpass}} - Band-pass filter.
\item
  \href{tseries/bwf}{\texttt{bwf}} - Butterworth filter with tunes.
\item
  \href{tseries/bwf2}{\texttt{bwf2}} - Swap output arguments of the
  Butterworth filter with tunes.
\item
  \href{tseries/detrend}{\texttt{detrend}} - Remove a linear time trend.
\item
  \href{tseries/expsmooth}{\texttt{expsmooth}} - Exponential smoothing.
\item
  \href{tseries/hpf}{\texttt{hpf}} - Hodrick-Prescott filter with tunes
  (aka LRX filter).
\item
  \href{tseries/hpf2}{\texttt{hpf2}} - Swap output arguments of the
  Hodrick-Prescott filter with tunes.
\item
  \href{tseries/fft}{\texttt{fft}} - Discrete Fourier transform of
  tseries object.
\item
  \href{tseries/llf}{\texttt{llf}} - Local level filter (aka random walk
  plus white noise) with tunes.
\item
  \href{tseries/llf2}{\texttt{llf2}} - Swap output arguments of the
  local linear trend filter with tunes.
\item
  \href{tseries/moving}{\texttt{moving}} - Apply function to moving
  window of observations.
\item
  \href{tseries/trend}{\texttt{trend}} - Estimate a time trend.
\item
  \href{tseries/x12}{\texttt{x12}} - Access to X13-ARIMA-SEATS seasonal
  adjustment program.
\end{itemize}

\paragraph{Estimation and sample
characteristics}

Note that most of the sample characteristics are listed above in the
Maths and statistics functions and operators section.

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{tseries/acf}{\texttt{acf}} - Sample autocovariance and
  autocorrelation functions.
\item
  \href{tseries/hpdi}{\texttt{hpdi}} - Highest probability density
  interval.
\item
  \href{tseries/chowlin}{\texttt{chowlin}} - Chow-Lin distribution of
  low-frequency observations over higher-frequency periods.
\item
  \href{tseries/regress}{\texttt{regress}} - Ordinary or weighted
  least-square regression.
\end{itemize}

\paragraph{Visualising tseries
objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{tseries/area}{\texttt{area}} - Area graph for tseries objects.
\item
  \href{tseries/band}{\texttt{band}} - Line-and-band graph for tseries
  objects.
\item
  \href{tseries/bar}{\texttt{bar}} - Bar graph for tseries objects.
\item
  \href{tseries/barcon}{\texttt{barcon}} - Contribution bar graph for
  tseries objects.
\item
  \href{tseries/errorbar}{\texttt{errorbar}} - Line plot with error
  bars.
\item
  \href{tseries/plot}{\texttt{plot}} - Line graph for tseries objects.
\item
  \href{tseries/plotcmp}{\texttt{plotcmp}} - Comparison graph for two
  time series.
\item
  \href{tseries/plotpred}{\texttt{plotpred}} - Plot Kalman filter
  predictions.
\item
  \href{tseries/plotyy}{\texttt{plotyy}} - Line plot function with LHS
  and RHS axes for time series.
\item
  \href{tseries/scatter}{\texttt{scatter}} - Scatter graph for tseries
  objects.
\item
  \href{tseries/spy}{\texttt{spy}} - Visualise tseries observations that
  pass a test.
\item
  \href{tseries/stem}{\texttt{stem}} - Plot tseries as discrete sequence
  data.
\end{itemize}

\paragraph{Manipulating tseries
objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{tseries/empty}{\texttt{empty}} - Empty time series preserving
  the size in 2nd and higher dimensions.
\item
  \href{tseries/permute}{\texttt{permute}} - Permute dimensions of a
  tseries object.
\item
  \href{tseries/redate}{\texttt{redate}} - Change time dimension of a
  tseries object.
\item
  \href{tseries/reshape}{\texttt{reshape}} - Reshape size of time series
  in 2nd and higher dimensions.
\item
  \href{tseries/resize}{\texttt{resize}} - Clip tseries object down to a
  specified date range.
\item
  \href{tseries/sort}{\texttt{sort}} - Sort tseries columns by specified
  criterion.
\end{itemize}

\paragraph{Converting tseries objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{tseries/convert}{\texttt{convert}} - Convert tseries object to a
  different frequency.
\item
  \href{tseries/double}{\texttt{double}} - Return tseries observations
  as double-precision numeric array.
\item
  \href{tseries/doubledata}{\texttt{doubledata}} - Convert tseries
  observations to double precision.
\item
  \href{tseries/single}{\texttt{single}} - Return tseries observations
  as single-precision numeric array.
\item
  \href{tseries/singledata}{\texttt{singledata}} - Convert tseries
  observations to single precision.
\end{itemize}

\paragraph{Other tseries functions}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{tseries/apct}{\texttt{apct}} - Annualised percent rate of
  change.
\item
  \href{tseries/bsxfun}{\texttt{bsxfun}} - Standard BSXFUN implemented
  for tseries objects.
\item
  \href{tseries/cumsumk}{\texttt{cumsumk}} - Cumulative sum with a
  k-period leap.
\item
  \href{tseries/destdise}{\texttt{destdise}} - Destandardise tseries
  object by applying specified standard deviation and mean to it.
\item
  \href{tseries/diff}{\texttt{diff}} - First difference.
\item
  \href{tseries/interp}{\texttt{interp}} - Interpolate missing
  observations.
\item
  \href{tseries/normalise}{\texttt{normalise}} - Normalise (or rebase)
  data to particular date.
\item
  \href{tseries/pct}{\texttt{pct}} - Percent rate of change.
\item
  \href{tseries/round}{\texttt{round}} - Round tseries values to
  specified number of decimals.
\item
  \href{tseries/rmse}{\texttt{rmse}} - Compute RMSE for given
  observations and predictions.
\item
  \href{tseries/stdise}{\texttt{stdise}} - Standardise tseries data by
  subtracting mean and dividing by std deviation.
\item
  \href{tseries/windex}{\texttt{windex}} - Simple weighted or Divisia
  index.
\item
  \href{tseries/wmean}{\texttt{wmean}} - Weighted average of time series
  observations.
\end{itemize}

\paragraph{Getting on-line help on tseries
functions}

\begin{verbatim}
help tseries
help tseries/function_name
\end{verbatim}



