

    \filetitle{convert}{Convert tseries object to a different frequency}{tseries/convert}

	\paragraph{Syntax}

\begin{verbatim}
Y = convert(X,NewFreq,...)
Y = convert(X,NewFreq,Range,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{X} {[} tseries {]} - Input tseries object that will be
  converted to a new frequency, \texttt{freq}, aggregating or
  intrapolating the data.
\item
  \texttt{NewFreq} {[} numeric \textbar{} char {]} - New frequency to
  which the input data will be converted: \texttt{1} or \texttt{'A'} for
  yearly, \texttt{2} or \texttt{'H'} for half-yearly, \texttt{4} or
  \texttt{'Q'} for quarterly, \texttt{6} or \texttt{'B'} for bi-monthly,
  and \texttt{12} or \texttt{'M'} for monthly.
\item
  \texttt{Range} {[} numeric {]} - Date range on which the input data
  will be converted.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{Y} {[} tseries {]} - Output tseries created by converting
  \texttt{X} to the new frequency.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'ignoreNaN='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Exclude NaNs from agreggation.
\item
  \texttt{'missing='} {[} numeric \textbar{} \emph{\texttt{NaN}}
  \textbar{} \texttt{'last'} {]} - Replace missing observations with
  this value.
\end{itemize}

\paragraph{Options for high- to low-frequency conversion
(aggregation)}

\begin{itemize}
\item
  \texttt{'method='} {[} function\_handle \textbar{} \texttt{'first'}
  \textbar{} \texttt{'last'} \textbar{} \emph{\texttt{@mean}} {]} -
  Method that will be used to aggregate the high frequency data.
\item
  \texttt{'select='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
  Select only these high-frequency observations within each
  low-frequency period; Inf means all observations will be used.
\end{itemize}

\paragraph{Options for low- to high-frequency conversion
(interpolation)}

\begin{itemize}
\item
  \texttt{'method='} {[} char \textbar{} \emph{\texttt{'cubic'}}
  \textbar{} \texttt{'quadsum'} \textbar{} \texttt{'quadavg'} {]} -
  Interpolation method; any option available in the built-in
  \texttt{interp1} function can be used.
\item
  \texttt{'position='} {[} \emph{\texttt{'centre'}} \textbar{}
  \texttt{'start'} \textbar{} \texttt{'end'} {]} - Position of the
  low-frequency date grid.
\end{itemize}

\paragraph{Description}

The function handle that you pass in through the `method' option when
you aggregate the data (convert higher frequency to lower frequency)
should behave like the built-in functions \texttt{mean}, \texttt{sum}
etc. In other words, it is expected to accept two input arguments:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  the data to be aggregated,
\item
  the dimension along which the aggregation is calculated.
\end{itemize}

The function will be called with the second input argument set to 1, as
the data are processed en block columnwise. If this call fails,
\texttt{convert} will attempt to call the function with just one input
argument, the data, but this is not a safe option under some
circumstances since dimension mismatch may occur.

\paragraph{Example}


