

    \filetitle{plotyy}{Line plot function with LHS and RHS axes for time series}{tseries/plotyy}

	\paragraph{Syntax}

\begin{verbatim}
[Ax,Lhs,Rhs,Range] = plotyy(X,Y,...)
[Ax,Lhs,Rhs,Range] = plotyy(Range,X,Y,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{Range} {[} numeric {]} - Date range; if not specified the
  entire range of the input tseries object will be plotted.
\item
  \texttt{X} {[} tseries {]} - Input tseries object whose columns will
  be plotted and labelled on the LHS.
\item
  \texttt{Y} {[} tseries {]} - Input tseries object whose columns will
  be plotted and labelled on the RHS.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{Ax} {[} handle \textbar{} numeric {]} - Handles to the LHS and
  RHS axes.
\item
  \texttt{Lhs} {[} handle \textbar{} numeric {]} - Handles to series
  plotted on the LHS axis.
\item
  \texttt{Rhs} {[} handle \textbar{} numeric {]} - Handles to series
  plotted on the RHS axis.
\item
  \texttt{Range} {[} handle \textbar{} numeric {]} - Actually plotted
  date range.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'coincide='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Make the LHS and RHS y-axis grids
  coincide.
\item
  \texttt{'lhsPlotFunc='} {[} \texttt{@area} \textbar{} \texttt{@bar}
  \textbar{} \emph{\texttt{@plot}} \textbar{} \texttt{@stem} {]} -
  Function that will be used to plot the LHS data.
\item
  \texttt{'lhsTight='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Make the LHS y-axis tight.
\item
  \texttt{'rhsPlotFunc='} {[} \texttt{@area} \textbar{} \texttt{@bar}
  \textbar{} \emph{\texttt{@plot}} \textbar{} \texttt{@stem} {]} -
  Function that will be used to plot the RHS data.
\item
  \texttt{'rhsTight='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Make the RHS y-axis tight.
\end{itemize}

See help on \href{tseries/plot}{\texttt{tseries/plot}} and the built-in
function \texttt{plotyy} for all options available.

\paragraph{Description}

\paragraph{Example}


