

    \filetitle{plotpred}{Plot Kalman filter predictions}{tseries/plotpred}

	\paragraph{Syntax}

\begin{verbatim}
[H1,H2,H3] = plotpred(X,Y,...)
[H1,H2,H3] = plotpred(Ax,X,Y,...)
[H1,H2,H3] = plotpred(Ax,Range,X,Y,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{X} {[} tseries {]} - Input data with time series observations.
\item
  \texttt{Y} {[} tseries {]} - Input data with predictions calculated in
  a Kalman filter run with an \texttt{'ahead='} option.
\item
  \texttt{Ax} {[} numeric {]} - Handle to axes object in which the data
  will be plotted.
\item
  \texttt{Range} {[} numeric \textbar{} Inf {]} - Date range on which
  the input data will be plotted.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{H1} {[} numeric {]} - Handles to a line object showing the
  time series observations (the first column, \texttt{X}, in the input
  data).
\item
  \texttt{H2} {[} numeric {]} - Handles to line objects showing the
  Kalman filter predictions (the second and further columns, \texttt{Y},
  in the input data).
\item
  \texttt{H3} {[} numeric {]} - Handles to one-point line objects
  displaying a marker at the start of each line.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'connect='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Connect the prediction lines, \texttt{Y}, with the corresponding
  observation in \texttt{X}.
\item
  \texttt{'firstMarker='} {[} \emph{\texttt{'none'}} \textbar{} char {]}
  - Type of marker displayed at the start of each prediction line.
\item
  \texttt{'showNaNLines='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Show or remove lines with whose starting points
  are NaN (missing observations).
\end{itemize}

See help on \href{tseries/plot}{\texttt{plot}} and on the built-in
function \texttt{plot} for options available.

\paragraph{Description}

\paragraph{Example}


