

    \filetitle{plotcmp}{Comparison graph for two time series}{tseries/plotcmp}

	\paragraph{Syntax}

\begin{verbatim}
[Ax,Lhs,Rhs] = plotcmp(X,...)
[Ax,Lhs,Rhs] = plotcmp(Range,X,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{Range} {[} numeric {]} - Date range; if not specified the
  entire range of the input tseries object will be plotted.
\item
  \texttt{X} {[} tseries {]} - Tseries object with two or more columns;
  the difference (between the second and the first column (or any other
  linear combination of its columns specified through the option
  \texttt{'compare='}) will be displayed as an RHS area or bar graph.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{Ax} {[} handle \textbar{} numeric {]} - Handles to the LHS and
  RHS axes.
\item
  \texttt{Lhs} {[} handle \textbar{} numeric {]} - Handles to the two
  original lines.
\item
  \texttt{Rhs} {[} handle \textbar{} numeric {]} - Handles to the area
  or bar difference graph.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'baseLine='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Draw a baseline in the bar/area difference graph.
\item
  \texttt{'compare='} {[} numeric \textbar{} \emph{\texttt{{[}-1;1{]}}}
  {]} - Linear combination of the observations that will be plotted in
  the RHS graph; \texttt{{[}-1;1{]}} means a difference between the
  second series and the first series, \texttt{X\{:,2\}-X\{:,1\}}.
\item
  \texttt{'cmpColor='} {[} numeric \textbar{}
  \emph{\texttt{{[}1,0.75,0.75{]}}} {]} - Color that will be used to
  plot the area or bar difference (comparison) graph.
\item
  \texttt{'cmpPlotFunc='} {[} \texttt{@area} \textbar{}
  \emph{\texttt{@bar}} {]} - Function that will be used to plot the
  difference (comparision) data on the RHS.
\end{itemize}

See help on \href{tseries/plotyy}{\texttt{tseries/plotyy}} for other
options available.

\paragraph{Description}

\paragraph{Example}


