

    \filetitle{x12}{Access to X13-ARIMA-SEATS seasonal adjustment program}{tseries/x12}

	\paragraph{Syntax with a single type of output
requested}

\begin{verbatim}
[Y,OutpFile,ErrFile,Model,X] = x12(X,...)
[Y,OutpFile,ErrFile,Model,X] = x12(X,Range,...)
\end{verbatim}

\paragraph{Syntax with mutliple types of output
requested}

\begin{verbatim}
[Y1,Y2,...,OutpFile,ErrFile,Model,X] = x12(X,Range,...)
\end{verbatim}

See the option \texttt{'output='} for the types of output data available
from X12.

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{X} {[} tseries {]} - Input data that will seasonally adjusted
  or filtered by the Census X12 Arima.
\item
  \texttt{Range} {[} numeric {]} - Date range on which the X12 will be
  run; if not specified or Inf the entire available range will be used.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{Y}, \texttt{Y1}, \texttt{Y2}, \ldots{} {[} tseries {]} -
  Requested output data, by default only one type of output is returned,
  the seasonlly adjusted data; see the option \texttt{'output='}.
\item
  \texttt{OutpFile} {[} cellstr {]} - Contents of the output log files
  produced by X12; each cell contains the log file for one type of
  output requested.
\item
  \texttt{ErrFile} {[} cellstr {]} - Contents of the error files
  produced by X12; each cell contains the error file for one type of
  output requested.
\item
  \texttt{Model} {[} struct {]} - Struct array with model specifications
  and parameter estimates for each of the ARIMA models fitted;
  \texttt{Model} matches the size of \texttt{X} is 2nd and higher
  dimensions.
\item
  \texttt{X} {[} tseries {]} - Original input data with forecasts and/or
  backcasts appended if the options \texttt{'forecast='} and/or
  \texttt{'backcast='} are used.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'backcast='} {[} numeric \textbar{} \emph{\texttt{0}} {]} -
  Run a backcast based on the fitted ARIMA model for this number of
  periods back to improve on the seasonal adjustment; see help on the
  \texttt{x11} specs in the X13-ARIMA-SEATS manual. The backcast is
  included in the output argument \texttt{X}.
\item
  \texttt{'cleanup='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Delete temporary X12 files when done; the temporary files are
  named \texttt{iris\_x12a.*}.
\item
  \texttt{'log='} {[} \texttt{true} \textbar{} \emph{\texttt{false}} {]}
  - Logarithmise the input data before, and de-logarithmise the output
  data back after, running \texttt{x12}.
\item
  \texttt{'forecast='} {[} numeric \textbar{} \emph{\texttt{0}} {]} -
  Run a forecast based on the fitted ARIMA model for this number of
  periods ahead to improve on the seasonal adjustment; see help on the
  \texttt{x11} specs in the X13-ARIMA-SEATS manual. The forecast is
  included in the output argument \texttt{X}.
\item
  \texttt{'display='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Display X12 output messages in command window; if false the
  messages will be saved in a TXT file.
\item
  \texttt{'dummy='} {[} tseries \textbar{} \emph{empty} {]} - User dummy
  variable or variables (in case of a multivariate tseries object) used
  in X13-ARIMA-SEATS regression; the dummy variables must also include
  values for forecasts and backcasts if you request them; the type of
  the dummy can be specified in the option \texttt{'dummyType='}.
\item
  \texttt{'dummyType='} {[} \texttt{'ao'} \textbar{}
  \emph{\texttt{'holiday'}} \textbar{} \texttt{'td'} {]} - Type of the
  user dummy (which is specified through the option \texttt{'dummy='});
  the three basic types of dummies are additive outlier (\texttt{'ao'}),
  holiday flows (\texttt{'holiday'}), and trading days (\texttt{'td'});
  see the X13-ARIMA-SEATS or X13-ARIMA documentation for more details
  (available from the U.S.Census Bureau website), look for the section
  on the REGRESSION spec, options `user' and `usertype'.
\item
  \texttt{'mode='} {[} \emph{\texttt{'auto'}} \textbar{} \texttt{'add'}
  \textbar{} \texttt{'logadd'} \textbar{} \texttt{'mult'} \textbar{}
  \texttt{'pseudoadd'} \textbar{} \texttt{'sign'} {]} - Seasonal
  adjustment mode (see help on the \texttt{x11} specs in the
  X13-ARIMA-SEATS manual); \texttt{'auto'} means that series with only
  positive or only negative numbers will be adjusted in the
  \texttt{'mult'} (multiplicative) mode, while series with combined
  positive and negative numbers in the \texttt{'add'} (additive) mode.
\item
  \texttt{'maxIter='} {[} numeric \textbar{} \emph{\texttt{1500}} {]} -
  Maximum number of iterations for the X12 estimation procedure. See
  help on the \texttt{estimation} specs in the X13-ARIMA-SEATS manual.
\item
  \texttt{'maxOrder='} {[} numeric \textbar{} \emph{\texttt{{[}2,1{]}}}
  {]} - A 1-by-2 vector with maximum order for the regular ARMA model
  (can be \texttt{1}, \texttt{2}, \texttt{3}, or \texttt{4}) and maximum
  order for the seasonal ARMA model (can be \texttt{1} or \texttt{2}).
  See help on the \texttt{automdl} specs in the X13-ARIMA-SEATS manual.
\item
  `missing=' {[} \texttt{true} \textbar{} \emph{\texttt{false}} {]} -
  Allow for in-sample missing observations, and fill in values predicted
  by an estimated ARIMA process; if \texttt{false}, the seasonal
  adjustment will not run and a warning will be thrown.
\item
  \texttt{'output='} {[} char \textbar{} cellstr \textbar{}
  \emph{\texttt{'SA'}} {]} - List of requested output data; the cellstr
  or comma-separated list can combine any number of the request
  specifications listed below in subsection Output request; See also
  help on the \texttt{x11} specs in the X13-ARIMA-SEATS manual.
\item
  \texttt{'saveAs='} {[} char \textbar{} \emph{empty} {]} - Name (or a
  whole path) under which X13-ARIMA-SEATS output files will be saved.
\item
  \texttt{'specFile='} {[} char \textbar{} \emph{\texttt{'default'}} {]}
  - Name of the X13-ARIMA-SEATS spec file; if \texttt{'default'} the
  IRIS default spec file will be used, see description.
\item
  \texttt{'tdays='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Correct for the number of trading days. See help on the
  \texttt{x11regression} specs in the X13-ARIMA-SEATS manual.
\item
  \texttt{'tempDir='} {[} char \textbar{} function\_handle \textbar{}
  \texttt{'.'} {]} - Directory in which X13-ARIMA-SEATS temporary files
  will be created; if the directory does not exist, it will be created
  at the beginning and deleted at the end of the execution (unless
  \texttt{'cleanup=' false}).
\item
  \texttt{'tolerance='} {[} numeric \textbar{} \emph{\texttt{1e-5}} {]}
  - Convergence tolerance for the X13 estimation procedure. See help on
  the \texttt{estimation} specs in the X13-ARIMA-SEATS manual.
\end{itemize}

\paragraph{Description}

\subparagraph{Output requests}

The option ``output=' can combine any number of the following requests:

\begin{itemize}
\item
  \texttt{'SA'} - seasonally adjusted series;
\item
  \texttt{'SF'} - seasonal factors;
\item
  \texttt{'TC'} - trend-cycle component;
\item
  \texttt{'IR'} - irregular component;
\item
  \texttt{'MV'} - the original input series with missing values fitted
  by running an estimated ARIMA model.
\end{itemize}

\subparagraph{Missing observations}

If you keep \texttt{'missing=' false} (this is the default for backward
compatibility), \texttt{x12} will not run on series with in-sample
missing observations, and a warning will be thrown.

If you set \texttt{'missing=' true}, you allow for in-sample missing
observations. The X13-ARIMA-SEATS program handles missing observations
by filling in values predicted by the estimated ARIMA process. You can
request the series with missing values filled in by including
\texttt{MV} in the option \texttt{'output='}.

\subparagraph{Spec file}

The default X13-ARIMA-SEATS spec file is
\texttt{+thirdparty/x12/default.spc}. You can create your own spec file
to include options that are not available through the IRIS interface.
You can use the following pre-defined placeholders letting IRIS fill in
some of the information needed (check out the default file):

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{\$series\_data\$} is replaced with a column vector of input
  observations;
\item
  \texttt{\$series\_freq\$} is replaced with a number representing the
  date frequency: either 4 for quarterly, or 12 for monthly (other
  frequencies are currenlty not supported by X13-ARIMA-SEATS);
\item
  \texttt{\$series\_startyear\$} is replaced with the start year of the
  input series;
\item
  \texttt{\$series\_startper\$} is replaced with the start quarter or
  month of the input series;
\item
  \texttt{\$transform\_function\$} is replaced with \texttt{log} or
  \texttt{none} depending on the mode selected by the user;
\item
  \texttt{\$forecast\_maxlead\$} is replaced with the requested number
  of ARIMA forecast periods used to extend the series before seasonal
  adjustment.
\item
  \texttt{\$forecast\_maxlead\$} is replaced with the requested number
  of ARIMA forecast periods used to extend the series before seasonal
  adjustment.
\item
  \texttt{\$tolerance\$} is replaced with the requested convergence
  tolerance in the \texttt{estimation} spec.
\item
  \texttt{\$maxiter\$} is replaced with the requested maximum number of
  iterations in the \texttt{estimation} spec.
\item
  \texttt{\$maxorder\$} is replaced with two numbers separated by a
  blank space: maximum order of regular ARIMA, and maximum order of
  seasonal ARIMA.
\item
  \texttt{\$x11\_mode\$} is replaced with the requested mode:
  \texttt{'add'} for additive, \texttt{'mult'} for multiplicative,
  \texttt{'pseudoadd'} for pseudo-additive, or \texttt{'logadd'} for
  log-additive;
\item
  \texttt{\$x12\_save\$} is replaced with the list of the requested
  output series: \texttt{'d10'} for seasonals, \texttt{'d11'} for final
  seasonally adjusted series, \texttt{'d12'} for trend-cycle,
  \texttt{'d13'} for irregular component.
\end{itemize}

Two of the placeholders, \texttt{'\$series\_data\$} and
\texttt{\$x12\_output\$}, are required; if they are not found in the
spec file, IRIS throws an error.

\subparagraph{Estimates of ARIMA model
parameters}

The ARIMA model specification, \texttt{Model}, is a struct with three
fields:

\begin{itemize}
\item
  \texttt{.spec} - a cell array with the first cell giving the structure
  of the non-seasonal ARIMA, and the second cell giving the structure of
  the seasonal ARIMA; both specifications follow the usual Box-Jenkins
  notation, e.g. \texttt{{[}0 1 1{]}}.
\item
  \texttt{.ar} - a numeric array with the point estimates of the AR
  coefficients (non-seasonal and seasonal).
\item
  \texttt{.ma} - a numeric array with the point estimates of the MA
  coefficients (non-seasonal and seasonal).
\end{itemize}

\paragraph{Example}

If you wish to run \texttt{x12} on the entire range on which the input
time series is defined, and do not use any options, you can omit the
second input argument (the date range). These following three calls to
\texttt{x12} do exactly the same:

\begin{verbatim}
xsa = x12(x);
xsa = x12(x,Inf);
xsa = x12(x,get(x,'range'));
\end{verbatim}

\paragraph{Example}

If you wish to specify some of the options, you have to enter a date
range or use \texttt{Inf}:

\begin{verbatim}
xsa = x12(x,Inf,'mode=','add');
\end{verbatim}


