

    \filetitle{fevd}{Forecast error variance decomposition for SVAR variables}{SVAR/fevd}

	\paragraph{Syntax}

\begin{verbatim}
[X,Y,XX,YY] = fevd(V,NPer)
[X,Y,XX,YY] = fevd(V,Range)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{V} {[} VAR {]} - Structural VAR model.
\item
  \texttt{NPer} {[} numeric {]} - Number of periods.
\item
  \texttt{Range} {[} numeric {]} - Date range.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{X} {[} namedmat \textbar{} numeric {]} - Forecast error
  variance decomposition into absolute contributions of residuals;
  absolute contributions sum up to the total variance.
\item
  \texttt{Y} {[} namedmat \textbar{} numeric {]} - Forecast error
  variance decomposition into relative contributions of residuals;
  relative contributions sum up to \texttt{1}.
\item
  \texttt{XX} {[} tseries {]} - Database with a tseries with absolute
  contributions in columns for each VAR variable.
\item
  \texttt{YY} {[} tseries {]} - Database with a tseries with relative
  contributions in columns for each VAR variable.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{'matrixFmt='} {[} \emph{\texttt{'namedmat'}} \textbar{}
  \texttt{'plain'} {]} - Return matrices \texttt{X} and \texttt{Y} as be
  either \href{namedmat/Contents}{\texttt{namedmat}} objects
  (i.e.~matrices with named rows and columns) or plain numeric arrays.
\end{itemize}

\paragraph{Description}

The output matrices \texttt{X} and \texttt{Y} are Ny-by-Ny-by-Nt-by-NAlt
namedmat objects (matrices with named rows and columns), where Ny is the
number of endogenous variables (and hence also structural residuals), Nt
is the number of periods, and NAlt is the number of alternative
parameterizations.

The output databases \texttt{XX} and \texttt{YY} contain
Nt-by-Ny-by-NAlt tseries objects (one for each endogenous variable).

\paragraph{Example}


