

    \filetitle{dbfun}{Apply function to database fields}{dbase/dbfun}

	\paragraph{Syntax}

\begin{verbatim}
[D,Flag,ErrList,WarnList] = dbfun(Func,D1,...)
[D,Flag,ErrList,WarnList] = dbfun(Func,D1,D2,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{Func} {[} function\_handle \textbar{} char {]} - Function that
  will be applied to each field.
\item
  \texttt{D1} {[} struct {]} - Input database.
\item
  \texttt{D2}, \texttt{D3}, \ldots{} {[} struct {]} - Further input
  databases when \texttt{Func} accepts two input arguments.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{D} {[} struct {]} - Output database whose fields will be
  created by applying \texttt{Func} to each field of the input database
  or databases.
\item
  \texttt{Flag} {[} \texttt{true} \textbar{} \texttt{false} {]} - True
  if no error occurs when evaluating the function.
\item
  \texttt{ErrList} {[} cellstr {]} - List of fields on which the
  function has thrown an error.
\item
  \texttt{WarnList} {[} cellstr {]} - List of fields on which the
  function has thrown a warning.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'cascade='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Cascade through subdatabases applying the function \texttt{Func}
  to their fields, too.
\item
  \texttt{'classList='} {[} cell \textbar{} cellstr \textbar{}
  \emph{\texttt{Inf}} {]} - Apply \texttt{Func} only to the fields of
  specified classes.
\item
  \texttt{'fresh='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Keep uprocessed fields in the output database.
\item
  \texttt{'nameList='} {[} cell \textbar{} cellstr \textbar{}
  \emph{\texttt{Inf}} {]} - Apply \texttt{Func} only to the specified
  field names; can be still combined with the option
  \texttt{'classList='}.
\item
  \texttt{'onError='} {[} \texttt{'keep'} \textbar{} \texttt{'NaN'}
  \textbar{} \emph{\texttt{'remove'}} {]}
\end{itemize}

\paragraph{Description}

\paragraph{Example}


