

    \filetitle{dbsave}{Save database as CSV file}{dbase/dbsave}

	\paragraph{Syntax}

\begin{verbatim}
List = dbsave(D,FName)
List = dbsave(D,FName,Dates,...)
\end{verbatim}

\paragraph{Output arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{List} {[} cellstr {]} - - List of actually saved database
  entries.
\end{itemize}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{D} {[} struct {]} - Database whose tseries and numeric entries
  will be saved.
\item
  \texttt{FName} {[} char {]} - Filename under which the CSV will be
  saved, including its extension.
\item
  \texttt{Dates} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} Dates or
  date range on which the tseries objects will be saved.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'class='} {[} \emph{\texttt{true}} \textbar{} false {]} -
  Include a row with class and size specifications.
\item
  \texttt{'comment='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Include a row with comments for tseries objects.
\item
  \texttt{'decimal='} {[} numeric \textbar{} \emph{empty} {]} - Number
  of decimals up to which the data will be saved; if empty the
  \texttt{'format'} option is used.
\item
  \texttt{'format='} {[} char \textbar{} \emph{\texttt{'\%.8e'}} {]} -
  Numeric format that will be used to represent the data, see
  \texttt{sprintf} for details on formatting, The format must start with
  a \texttt{'\%'}, and must not include identifiers specifying order of
  processing, i.e.~the \texttt{'\$'} signs, or left-justify flags, the
  \texttt{'-'} signs.
\item
  \texttt{'freqLetters='} {[} char \textbar{} \emph{\texttt{'YHQBM'}}
  {]} - Five letters to represent the five possible date frequencies
  (annual, semi-annual, quarterly, bimonthly, monthly).
\item
  \texttt{'matchFreq='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Save only the tseries whose date
  frequencies match the input vector of dates, \texttt{Dates}.
\item
  \texttt{'nan='} {[} char \textbar{} \emph{\texttt{'NaN'}} {]} - String
  that will be used to represent NaNs.
\item
  \texttt{'saveSubdb='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Save sub-databases (structs found within
  the struct \texttt{D}); the sub-databases will be saved to separate
  CSF files.
\item
  \texttt{'userData='} {[} char \textbar{} \emph{`userdata'} {]} - Field
  name from which any kind of userdata will be read and saved in the CSV
  file.
\end{itemize}

\paragraph{Description}

The data saved include also imaginary parts of complex numbers.

\subparagraph{Saving user data with the
database}

If your database contains field named \texttt{'userdata='}, this will be
saved in the CSV file on a separate row. The \texttt{'userdata='} field
can be any combination of numeric, char, and cell arrays and 1-by-1
structs.

You can use the \texttt{'userdata='} field to describe the database or
preserve any sort of metadata. To change the name of the field that is
treated as user data, use the \texttt{'userData='} option.

\paragraph{Example}

Create a simple database with two time series.

\begin{verbatim}
d = struct();
d.x = tseries(qq(2010,1):qq(2010,4),@rand);
d.y = tseries(qq(2010,1):qq(2010,4),@rand);
\end{verbatim}

Add your own description of the database, e.g.

\begin{verbatim}
d.userdata = {'My database',datestr(now())};
\end{verbatim}

Save the database as CSV using \texttt{dbsave},

\begin{verbatim}
dbsave(d,'mydatabase.csv');
\end{verbatim}

When you later load the database,

\begin{verbatim}
d = dbload('mydatabase.csv')

d = 

   userdata: {'My database'  '23-Sep-2011 14:10:17'}
          x: [4x1 tseries]
          y: [4x1 tseries]
\end{verbatim}

the database will preserve the \texttt{'userdata='} field.

\paragraph{Example}

To change the field name under which you store your own user data, use
the \texttt{'userdata='} option when running \texttt{dbsave},

\begin{verbatim}
d = struct();
d.x = tseries(qq(2010,1):qq(2010,4),@rand);
d.y = tseries(qq(2010,1):qq(2010,4),@rand);
d.MYUSERDATA = {'My database',datestr(now())};
dbsave(d,'mydatabase.csv',Inf,'userData=','MYUSERDATA');
\end{verbatim}

The name of the user data field is also kept in the CSV file so that
\texttt{dbload} works fine in this case, too, and returns a database
identical to the saved one,

\begin{verbatim}
d = dbload('mydatabase.csv')

d = 

   MYUSERDATA: {'My database'  '23-Sep-2011 14:10:17'}
            x: [4x1 tseries]
            y: [4x1 tseries]
\end{verbatim}


