

    \filetitle{xls2csv}{Convert XLS file to CSV file}{dbase/xls2csv}

	\paragraph{Syntax}

\begin{verbatim}
xls2csv(InpFile)
xls2csv(InpFile,OutpFile,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{InpFile} {[} char {]} - Name of an XLS input file that will be
  converted to CSV.
\item
  \texttt{OutpFile} {[} empty \textbar{} char {]} - Name of the CSV
  output file; if not supplied or empty, the CSV file name will be
  derived from the XLS input file name.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{'sheet='} {[} numeric \textbar{} char \textbar{}
  \emph{\texttt{1}} {]} - Worksheet in the XLS file that will be saved;
  can be either the sheet number or the sheet name.
\end{itemize}

\paragraph{Description}

This function calls a third-party JavaScript (courtesy of Christopher
West). The script uses an MS Excel application on the background, and
hence MS Excel must be installed on the computer.

Only one worksheet at a time can be saved to CSV. By default, it is the
first worksheet found in the input XLS file; use the option
\texttt{'sheet='} to control which worksheet will be saved.

See also \$irisroot/+thirdparty/xls2csv.js for copyright information.

\paragraph{Example}

Save the first worksheets of the following XLS files to CSV files.

\begin{verbatim}
xls2csv('myDataFile.xls');
xls2csv('C:\Data\myDataFile.xls');
\end{verbatim}

\paragraph{Example}

Save the worksheet named `Sheet3' to a CSV file; the name of the CSV
file will be \texttt{'myDataFile.csv'}.

\begin{verbatim}
xls2csv('myDataFile.xls',[],'sheet=','Sheet3');
\end{verbatim}

\paragraph{Example}

Save the second worksheet to a CSV file under the name
\texttt{'myDataFile\_2.csv'}.

\begin{verbatim}
xls2csv('myDataFile.xls','myDataFile_2.csv,'sheet=',2);
\end{verbatim}


