

    \filetitle{estimate}{Estimate model parameters by optimising selected objective function}{model/estimate}

	\paragraph{Syntax}

\begin{verbatim}
[PEst,Pos,Cov,Hess,M,V,Delta,PDelta] = estimate(M,D,Range,Est,...)
[PEst,Pos,Cov,Hess,M,V,Delta,PDelta] = estimate(M,D,Range,Est,SPr,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{M} {[} model {]} - Model object.
\item
  \texttt{D} {[} struct \textbar{} cell {]} - Input database or datapack
  from which the measurement variables will be taken.
\item
  \texttt{Range} {[} struct {]} - Date range.
\item
  \texttt{Est} {[} struct {]} - Database with the list of paremeters
  that will be estimated, and the parameter prior specifications (see
  below).
\item
  \texttt{SPr} {[} empty \textbar{} systempriors {]} - System priors
  object, \href{systempriors/Contents}{\texttt{systempriors}}.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{PEst} {[} struct {]} - Database with point estimates of
  requested parameters.
\item
  \texttt{Pos} {[} poster {]} - Posterior,
  \href{poster/Contents}{\texttt{poster}}, object; this object also
  gives you access to the value of the objective function at optimum or
  at any point in the parameter space, see the
  \href{poster/eval}{\texttt{poster/eval}} function.
\item
  \texttt{Cov} {[} numeric {]} - Approximate covariance matrix for the
  estimates of parameters with slack bounds based on the asymptotic
  Fisher information matrix (not on the Hessian returned from the
  optimization routine).
\item
  \texttt{Hess} {[} cell {]} - \texttt{Hess\{1\}} is the total hessian
  of the objective function; \texttt{Hess\{2\}} is the contributions of
  the priors to the hessian.
\item
  \texttt{M} {[} model {]} - Model object solved with the estimated
  parameters (including out-of-likelihood parameters and common variance
  factor).
\end{itemize}

The remaining three output arguments, \texttt{V}, \texttt{Delta},
\texttt{PDelta}, are the same as the
\href{model/loglik}{\texttt{model/loglik}} output arguments of the same
names.

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'chkSstate='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} \textbar{} cell {]} - Check steady state in each
  iteration; works only in non-linear models.
\item
  \texttt{'evalFrfPriors='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - In each iteration, evaluate frequency response
  function prior density, and include it to the overall objective
  function to be optimised.
\item
  \texttt{'evalLik='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - In each iteration, evaluate likelihood (or another data based
  criterion), and include it to the overall objective function to be
  optimised.
\item
  \texttt{'evalPPriors='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - In each iteration, evaluate parameter prior
  density, and include it to the overall objective function to be
  optimised.
\item
  \texttt{'evalSPriors='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - In each iteration, evaluate system prior density,
  and include it to the overall objective function to be optimised.
\item
  \texttt{'filter='} {[} cell \textbar{} \emph{empty} {]} - Cell array
  of options that will be passed on to the Kalman filter including the
  type of objective function; see help on
  \href{model/filter}{\texttt{model/filter}} for the options available.
\item
  \texttt{'initVal='} {[} \texttt{model} \textbar{}
  \emph{\texttt{struct}} \textbar{} struct {]} - If \texttt{struct} use
  the values in the input struct \texttt{Est} to start the iteration; if
  \texttt{model} use the currently assigned parameter values in the
  input model, \texttt{M}.
\item
  \texttt{'maxIter='} {[} numeric \textbar{} \emph{\texttt{500}} {]} -
  Maximum number of iterations allowed.
\item
  \texttt{'maxFunEvals='} {[} numeric \textbar{} \emph{\texttt{2000}}
  {]} - Maximum number of objective function calls allowed.
\item
  \texttt{'noSolution='} {[} \emph{\texttt{'error'}} \textbar{}
  \texttt{'penalty'} \textbar{} numeric {]} - Specifies what happens if
  solution or steady state fails to solve in an iteration:
  \texttt{'error='} stops the execution with an error message,
  \texttt{'penalty='} returns an extreme value, \texttt{1e10}, back into
  the minimization routine; or a user-supplied penalty can be specified
  as a numeric scalar greater than \texttt{1e10}.
\item
  \texttt{'optimSet='} {[} cell \textbar{} \emph{empty} {]} - Cell array
  used to create the Optimization Toolbox options structure; works only
  with the option \texttt{'optimiser='} \texttt{'default'}.
\item
  \texttt{'refresh='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Refresh dynamic links in each iteration.
\item
  \texttt{'solve='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  \textbar{} cellstr {]} - Re-compute solution in each iteration; you
  can specify a cell array with options for the \texttt{solve} function.
\item
  \texttt{'optimiser='} {[} \emph{\texttt{'default'}} \textbar{}
  \texttt{'pso'} \textbar{} cell \textbar{} function\_handle {]} -
  Minimiz ation procedure.

  \begin{itemize}
  \item
    \texttt{'default'}: The Optimization Toolbox function
    \texttt{fminunc} or \texttt{fmincon} will be called depending on the
    presence or absence of lower and/or upper bounds.
  \item
    \texttt{'pso'}: The Particle Swarm Optimizer will be called; use the
    option \texttt{'pso='} to specify further options to control the
    optimizer (see Options for Particle Swarm Optimizer below).
  \item
    function\_handle or cell: Enter a function handle to your own
    optimization procedure, or a cell array with a function handle and
    additional input arguments (see below).
  \end{itemize}
\item
  \texttt{'sstate='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  \textbar{} cell \textbar{} function\_handle {]} - Re-compute steady
  state in each iteration; you can specify a cell array with options for
  the \texttt{sstate} function, or a function handle whose behaviour is
  described below.
\item
  \texttt{'tolFun='} {[} numeric \textbar{} \emph{\texttt{1e-6}} {]} -
  Termination tolerance on the objective function.
\item
  \texttt{'tolX='} {[} numeric \textbar{} \emph{\texttt{1e-6}} {]} -
  Termination tolerance on the estimated parameters.
\end{itemize}

\paragraph{Options for Particle Swarm
Optimizer}

The following options can be specified through the main option
\texttt{'optimset='} when \texttt{'optimiser=pso'}.

\begin{itemize}
\item
  \texttt{'cognitiveAttraction='} {[} numeric \textbar{}
  \emph{\texttt{0.5}} {]} - Scalar between \texttt{0} and \texttt{1} to
  control the relative attraction to the best location a particle can
  remember.
\item
  \texttt{'constrBoundary='} {[} \texttt{absorb} \textbar{}
  \emph{\texttt{reflect}} \textbar{} \texttt{soft} {]} - Controls the
  way imposed constraints are handled when violated.

  \begin{itemize}
  \item
    \texttt{'soft'}: Particles are allowed to travel outside the bounds
    but get bad fitness function (likelihood) values when they do;
  \item
    \texttt{'reflect'}: Particle velocity is changed such that when the
    particle encounters the bound its velocity is changed to effectively
    make it bounce off of the boundary;
  \item
    \texttt{'absorb'}: Particles hit the bound and stay at the bound
    until attracted elsewhere because its velocity is set to zero.
  \end{itemize}
\item
  \texttt{'display='} {[} \texttt{'off'} \textbar{} \texttt{'final'}
  \textbar{} \emph{\texttt{'iter'}} {]} - Level of display in order of
  increasing verbosity; \texttt{'iter'} will only produce output at most
  \texttt{'updateInterval='} seconds.
\item
  \texttt{'fitnessLimit='} {[} numeric \textbar{} \emph{\texttt{-Inf}}
  {]} - Algorithm will terminate when a function value this low is
  encountered.
\item
  \texttt{'generations='} {[} numeric \textbar{} \emph{\texttt{1000}}
  {]} - Positive integer describing the maximum length of swarm
  evolution.
\item
  \texttt{'hybridFcn='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} \textbar{} \texttt{'fmincon'} \textbar{}
  \texttt{'fminunc'} \textbar{} cell {]} - Run a second stage
  optimization after PSO (only available with the Optimization Tbx
  installed):

  \begin{itemize}
  \item
    \texttt{false}: No second stage optimization, run the particle swarm
    only.
  \item
    \texttt{true}: After PSO, run either \texttt{fminunc} or
    \texttt{fmincon}, the Optimization Toolbox routines, depending on
    the presence or absence of lower and upper bounds on estimated
    parameters.
  \item
    \texttt{'fminunc'}, \texttt{'fmincon'}: After PSO, run the specified
    Optimization Toolbox routine.
  \item
    cell: A cell array in which the first argument specifies the
    function as previously and the second argument contains the options
    structure for that function; for instance
    \texttt{\{@fmincon,optimset('Display','iter')\}}.
  \end{itemize}
\item
  \texttt{'includeInitialValue='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Include the initial vector of parameters in the
  initial population.
\item
  \texttt{'initialPopulation=}' {[} numeric \textbar{} \emph{empty} {]}
  - An NPar-by-NPop array containing the initial distribution of
  particles, where NPar is the number of estimated parameters, and NPop
  is the size of population. If empty, a population will be created
  containing the initial parameter vector and the rest of the particles
  will be randomly generated according to \texttt{'popInitRange='}. Use
  the option \texttt{'includeInitialValue=' false} oo exclude the
  initial value from the initial population so that the entire
  population is randomly generated.
\item
  \texttt{'socialAttraction='} {[} numeric \textbar{}
  \emph{\texttt{1.25}} {]} - Positive scalar to control the relative
  attraction of each particle to the best location they have heard about
  from other particles.
\item
  \texttt{'plotFcns='} {[} cell \textbar{} \emph{empty} {]} - Cell array
  of function handles to functions which accept
  \texttt{(options,state,flag)} values as input arguments. The only
  built-in general-purpose plotting function is
  \texttt{@optim.scoreDiversity}.
\item
  \texttt{'populationSize='} {[} numeric \textbar{} \emph{\texttt{40}}
  {]} - Positive integer which determines the number of particles in the
  swarm.
\item
  \texttt{'popInitRange='} {[} numeric \textbar{} \emph{empty} {]} - A
  2-by-NPar array which sets the range over which the initial population
  will be distributed, where NPar is the number of estimated parameters,
  or a 2-by-1 array with the range for all parameters. If empty and
  \texttt{'PopInitRange='} is not set, the upper and lower bounds will
  be used if both are finite. If either of the bounds are infinite, the
  range will be \texttt{{[}0;1{]}}.
\item
  \texttt{'stallGenLimit='} {[} numeric \textbar{} \emph{\texttt{100}}
  {]} - Maximum number of swarm iterations which result in no
  improvement in the fitness function (likelihood) value before the
  algorithm terminates.
\item
  \texttt{'timeLimit='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
  Maximum running time in seconds.
\item
  \texttt{'tolCon='} {[} numeric \textbar{} \emph{\texttt{1e-6}} {]} -
  Largest tolerated constraint violation.
\item
  \texttt{'tolFun='} {[} numeric \textbar{} \emph{\texttt{1e-6}} {]} -
  Function tolerance; when the change in the best fitness function value
  (likelihood) improvement per generation falls below this value the
  algorithm will terminate.
\item
  \texttt{'velocityLimit='} {[} numeric \textbar{} \emph{\texttt{Inf}}
  {]} - Positive scalar to bound particle intertia from above.
\item
  \texttt{'updateInterval='}* {[} numeric \textbar{} \texttt{5} {]} -
  Minimum length of time in seconds which must pass before new command
  window output will be produced.
\item
  \texttt{'useParallel='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Use a \texttt{parfor} loop which requires
  you already have a \texttt{matlabpool} open. Overhead is slightly
  higher for constrained problems than unconstrained problems.
\end{itemize}

\paragraph{Description}

The parameters that are to be estimated are specified in the input
parameter estimation database, \texttt{E} in which you can provide the
following specifications for each parameter:

\begin{verbatim}
E.parameter_name = { start, lower, upper, logpriorFunc };
\end{verbatim}

where \texttt{start} is the value from which the numerical optimization
will start, \texttt{lower} is the lower bound, \texttt{upper} is the
upper bound, and \texttt{logpriorFunc} is a function handle expected to
return the log of the prior density. You can use the
\href{logdist/Contents}{\texttt{logdist}} package to create function
handles for some of the basic prior distributions.

You can use \texttt{NaN} for \texttt{start} if you wish to use the value
currently assigned in the model object. You can use \texttt{-Inf} and
\texttt{Inf} for the bounds, or leave the bounds empty or not specify
them at all. You can leave the prior distribution empty or not specify
it at all.

\subparagraph{Estimating nonlinear
models}

By default, only the first-order solution, but not the steady state is
updated (recomputed) in each iteration before the likelihood is
evaluated. This behavior is controled by two options, \texttt{'solve='}
(\texttt{true} by default) and \texttt{'sstate='} (\texttt{false} by
default). If some of the estimated parameters do affect the steady state
of the model, the option '\texttt{sstate='} needs to be set to
\texttt{true} or to a cell array with steady-state options, as in the
function \href{model/sstate}{\texttt{sstate}}, otherwise the results
will be groslly inaccurate or a valid first-order solution will be
impossible to find.

When steady state is recomputed in each iteration, you may also want to
use the option \texttt{'chksstate='} to require that a steady-state
check for all model equations be performed.

\subparagraph{User-supplied optimization (minimization)
routine}

You can supply a function handle to your own minimization routine
through the option \texttt{'optimiser='}. This routine will be used
instead of the Optim Tbx's \texttt{fminunc} or \texttt{fmincon}
functions. The user-supplied function is expected to take at least five
input arguments and return three output arguments:

\begin{verbatim}
[PEst,ObjEst,Hess] = yourminfunc(F,P0,PLow,PHigh,OptimSet)
\end{verbatim}

with the following input arguments:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{F} is a function handle to the function minimised;
\item
  \texttt{P0} is a 1-by-N vector of initial parameter values;
\item
  \texttt{PLow} is a 1-by-N vector of lower bounds (with \texttt{-Inf}
  indicating no lower bound);
\item
  \texttt{PHigh} is a 1-by-N vector of upper bounds (with \texttt{Inf}
  indicating no upper bounds);
\item
  \texttt{OptimSet} is a cell array with name-value pairs entered by the
  user through the option \texttt{'optimSet='}. This option can be used
  to modify various settings related to the optimization routine, such
  as tolerance, number of iterations, etc. Of course, you may simply
  ignore it and leave this input argument unused;
\end{itemize}

and the following output arguments:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{PEst} is a 1-by-N vector of estimated parameters;
\item
  \texttt{ObjEst} is the value of the objective function at optimum;
\item
  \texttt{Hess} is a N-by-N approximate Hessian matrix at optimum.
\end{itemize}

If you need to use extra input arguments in your minimization function,
enter a cell array instead of a plain function handle:

\begin{verbatim}
{@yourminfunc,Arg1,Arg2,...}
\end{verbatim}

In that case, the optimiser will be called the following way:

\begin{verbatim}
[PEst,ObjEst,Hess] = yourminfunc(F,P0,PLow,PHigh,Opt,Arg1,Arg2,...)
\end{verbatim}

\subparagraph{User-supplied steady-state
solver}

You can supply a function handle to your own steady-state solver (i.e.~a
function that finds the steady state for given parameters) through the
\texttt{'sstate='} option.

The function is expected to take one input argument, the model object
with newly assigned parameters, and return at least two output
arguments, the model object with a new steady state (or balanced-growth
path) and a success flag. The flag is \texttt{true} if the steady state
has been successfully computed, and \texttt{false} if not:

\begin{verbatim}
[M,Success] = mysstatesolver(M)
\end{verbatim}

It is your responsibility to add the growth characteristics if some of
the model variables drift over time. In other words, you need to take
care of the imaginary parts of the steady state values in the model
object returned by the solver.

Alternatively, you can also run the steady-state solver with extra input
arguments (with the model object still being the first input argument).
In that case, you need to set the option \texttt{'sstate='} to a cell
array with the function handle in the first cell, and the other input
arguments afterwards, e.g.

\begin{verbatim}
'sstate=',{@mysstatesolver,1,'a',X}
\end{verbatim}

The actual function call will have the following form:

\begin{verbatim}
[M,Success] = mysstatesolver(M,1,'a',X)
\end{verbatim}

\paragraph{Example}


