

    \filetitle{fevd}{Forecast error variance decomposition for model variables}{model/fevd}

	\paragraph{Syntax}

\begin{verbatim}
[X,Y,List,A,B] = fevd(M,Range,...)
[X,Y,List,A,B] = fevd(M,NPer,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{M} {[} model {]} - Model object for which the decomposition
  will be computed.
\item
  \texttt{Range} {[} numeric {]} - Decomposition date range with the
  first date beign the first forecast period.
\item
  \texttt{NPer} {[} numeric {]} - Number of periods for which the
  decomposition will be computed.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{X} {[} namedmat \textbar{} numeric {]} - Array with the
  absolute contributions of individual shocks to total variance of each
  variables.
\item
  \texttt{Y} {[} namedmat \textbar{} numeric {]} - Array with the
  relative contributions of individual shocks to total variance of each
  variables.
\item
  \texttt{List} {[} cellstr {]} - List of variables in rows of the
  \texttt{X} an \texttt{Y} arrays, and shocks in columns of the
  \texttt{X} and \texttt{Y} arrays.
\item
  \texttt{A} {[} struct {]} - Database with the absolute contributions
  converted to time series.
\item
  \texttt{B} {[} struct {]} - Database with the relative contributions
  converted to time series.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'matrixFmt='} {[} \emph{\texttt{'namedmat'}} \textbar{}
  \texttt{'plain'} {]} - Return matrices \texttt{X} and \texttt{Y} as be
  either \href{namedmat/Contents}{\texttt{namedmat}} objects
  (i.e.~matrices with named rows and columns) or plain numeric arrays.
\item
  \texttt{'select='} {[} \texttt{@all} \textbar{} char \textbar{}
  cellstr {]} - Return FEVD for selected variables and/or shocks only;
  \texttt{@all} means all variables and shocks; this option does not
  apply to the output databases, \texttt{A} and \texttt{B}.
\end{itemize}

\paragraph{Description}

\paragraph{Example}


