

    \filetitle{ffrf}{Filter frequency response function of transition variables to measurement variables}{model/ffrf}

	\paragraph{Syntax}

\begin{verbatim}
[F,List] = ffrf(M,Freq,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{M} {[} model {]} - Model object for which the frequency
  response function will be computed.
\item
  \texttt{Freq} {[} numeric {]} - Vector of frequencies for which the
  response function will be computed.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{F} {[} namedmat \textbar{} numeric {]} - Array with frequency
  responses of transition variables (in rows) to measurement variables
  (in columns).
\item
  \texttt{List} {[} cell {]} - List of transition variables in rows of
  the \texttt{F} matrix, and list of measurement variables in columns of
  the \texttt{F} matrix.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'include='} {[} char \textbar{} cellstr \textbar{}
  \emph{\texttt{@all}} {]} - Include the effect of the listed
  measurement variables only; \texttt{@all} means all measurement
  variables.
\item
  \texttt{'exclude='} {[} char \textbar{} cellstr \textbar{}
  \emph{empty} {]} - Remove the effect of the listed measurement
  variables.
\item
  \texttt{'maxIter='} {[} numeric \textbar{} \emph{500} {]} - Maximum
  number of iteration when computing the steady-state Kalman filter.
\item
  \texttt{'matrixFmt='} {[} \emph{\texttt{'namedmat'}} \textbar{}
  \texttt{'plain'} {]} - Return matrix \texttt{F} as either a
  \href{namedmat/Contents}{\texttt{namedmat}} object (i.e.~matrix with
  named rows and columns) or a plain numeric array.
\item
  \texttt{'select='} {[} \emph{\texttt{@all}} \textbar{} char \textbar{}
  cellstr {]} - Return FFRF for selected variables only; \texttt{@all}
  means all variables.
\item
  \texttt{'tolerance='} {[} numeric \textbar{} \emph{\texttt{1e-7}} {]}
  - Convergence tolerance when computing the steady-state Kalman filter.
\end{itemize}

\paragraph{Description}

\paragraph{Example}


