

    \filetitle{fisher}{Approximate Fisher information matrix in frequency domain}{model/fisher}

	\paragraph{Syntax}

\begin{verbatim}
[F,FF,Delta,Freq] = fisher(M,NPer,PList,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{M} {[} model {]} - Solved model object.
\item
  \texttt{NPer} {[} numeric {]} - Length of the hypothetical range for
  which the Fisher information will be computed.
\item
  \texttt{PList} {[} cellstr {]} - List of parameters with respect to
  which the likelihood function will be differentiated.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{F} {[} numeric {]} - Approximation of the Fisher information
  matrix.
\item
  \texttt{FF} {[} numeric {]} - Contributions of individual frequencies
  to the total Fisher information matrix.
\item
  \texttt{Delta} {[} numeric {]} - Kronecker delta by which the
  contributions in \texttt{Fi} need to be multiplied to sum up to
  \texttt{F}.
\item
  \texttt{Freq} {[} numeric {]} - Vector of frequencies at which the
  Fisher information matrix is evaluated.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'chkSstate='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} \textbar{} cell {]} - Check steady state in each
  iteration; works only in non-linear models.
\item
  \texttt{'deviation='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Exclude the steady state effect at zero
  frequency.
\item
  \texttt{'exclude='} {[} char \textbar{} cellstr \textbar{}
  \emph{empty} {]} - List of measurement variables that will be excluded
  from the likelihood function.
\item
  \texttt{'percent='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Report the overall Fisher matrix \texttt{F} as Hessian w.r.t.
  the log of variables; the interpretation for this is that the Fisher
  matrix describes the changes in the log-likelihood function in reponse
  to percent, not absolute, changes in parameters.
\item
  \texttt{'progress='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Display progress bar in the command
  window.
\item
  \texttt{'refresh='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Refresh dynamic links in each differentiation step.
\item
  \texttt{'solve='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  \textbar{} cellstr {]} - Re-compute solution in each differentiation
  step; you can specify a cell array with options for the \texttt{solve}
  function.
\item
  \texttt{'sstate='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  \textbar{} cell {]} - Re-compute steady state in each differentiation
  step; if the model is non-linear, you can pass in a cell array with
  opt used in the \texttt{sstate} function.
\end{itemize}

\paragraph{Description}

\paragraph{Example}


