

    \filetitle{loglik}{Evaluate minus the log-likelihood function in time or frequency domain}{model/loglik}

	\paragraph{Full syntax}

\begin{verbatim}
[Obj,V,F,PE,Delta,PDelta] = loglik(M,D,Range,...)
\end{verbatim}

\paragraph{Syntax for fast one-off likelihood
evaluation}

\begin{verbatim}
Obj = loglik(M,D,Range,...)
\end{verbatim}

\paragraph{Syntax for repeated fast likelihood
evaluations}

\begin{verbatim}
% Step #1: Initialise.
loglik(M,D,Range,...,'persist=',true);

% Step #2: Assign/change parameters.
M... = ...; % Change parameters.

% Step #3: Re-compute steady state and solution if necessary.
M = ...;
M = ...;

% Step #4: Evaluate likelihood.
L = loglik(M);

% Repeat steps #2, #3, #4 for different values of parameters.
% ...
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{M} {[} model {]} - Model object on which the likelihood of the
  input data will be evaluated.
\item
  \texttt{D} {[} struct \textbar{} cell {]} - Input database or datapack
  from which the measurement variables will be taken.
\item
  \texttt{Range} {[} numeric {]} - Date range.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{Obj} {[} numeric {]} - Value of minus the log-likelihood
  function (or other objective function if specified in options).
\item
  \texttt{V} {[} numeric {]} - Estimated variance scale factor if the
  \texttt{'relative='} options is true; otherwise \texttt{V} is 1.
\item
  \texttt{F} {[} numeric {]} - Sequence of forecast MSE matrices for
  measurement variables.
\item
  \texttt{PE} {[} struct {]} - Database with prediction errors for
  measurement variables; exp of prediction errors for measurement
  variables declared as log variables.
\item
  \texttt{Delta} {[} struct {]} - Databse with point estimates of the
  deterministic trend parameters specified in the \texttt{'outoflik='}
  option.
\item
  \texttt{PDelta} {[} numeric {]} - MSE matrix of the estimates of the
  \texttt{'outoflik='} parameters.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'objDecomp='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Decompose the objective function into the
  contributions of individual time periods (in time domain) or
  individual frequencies (in frequency domain); the contributions are
  added as extra rows in the output argument \texttt{Obj}.
\item
  \texttt{'persist='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} -- Pre-process and store the overhead (data and options) for
  subsequent fast calls.
\end{itemize}

See help on \href{model/filter}{\texttt{model/filter}} for other options
available.

\paragraph{Description}

The number of output arguments you request when calling \texttt{loglik}
affects computational efficiency. Running the function with only the
first output argument, i.e.~the value of the likelihood function (minus
the log of it, in fact), results in the fastest performance.

The \texttt{loglik} function runs an identical Kalman filter as
\href{model/filter}{\texttt{model/filter}}, the only difference is the
types and order of output arguments returned.

\subparagraph{Fast evaluation of
likelihood}

Every time you change the parameters, you need to update the steady
state and solution of the model if necessary by yourself, before calling
\texttt{loglik}. Follow these rules:

\begin{itemize}
\item
  If you only change std deviations and no other parameters, you don't
  have to re-calculate steady state or solution.
\item
  If the model is linear, you only need to call
  \href{model/solve}{\texttt{solve}}.
\item
  The only exception to rules \#2 and \#3 is when the model has
  \href{modellang/links}{\texttt{dynamic links}} with references to some
  steady state values. In that case, you must also run
  \href{model/sstate}{\texttt{sstate}} after
  \href{model/solve}{\texttt{solve}} in linear models to update the
  steady state.
\item
  If the model is non-linear, and you only change parameters that affect
  transitory dynamics and not the steady state, you only need to call
  \href{model/solve}{\texttt{solve}}.
\item
  If the model is non-linear, and you change parameters that affect both
  transitory dynamics and steady state, you must run first
  \href{model/sstate}{\texttt{sstate}} and then
  \href{model/solve}{\texttt{solve}}.
\end{itemize}

\paragraph{Example}


