

    \filetitle{lognormal}{Characteristics of log-normal distributions returned from filter of forecast}{model/lognormal}

	\paragraph{Syntax}

\begin{verbatim}
D = lognormal(M,D,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{M} {[} model {]} - Model on which the \texttt{filter} or
  \texttt{forecast} function has been run.
\item
  \texttt{D} {[} struct {]} - Struct or database returned from the
  \texttt{filter} or \texttt{forecast} function.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{D} {[} struct {]} - Struct including new sub-databases with
  requested log-normal statistics.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'fresh='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Output structure will include only the newly computed databases.
\item
  \texttt{'mean='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Compute the mean of the log-normal distributions.
\item
  \texttt{'median='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Compute the median of the log-normal distributions.
\item
  \texttt{'mode='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Compute the mode of the log-normal distributions.
\item
  \texttt{'prctile='} {[} numeric \textbar{} \emph{\texttt{{[}5,95{]}}}
  {]} - Compute the selected percentiles of the log-normal
  distributions.
\item
  \texttt{'prefix='} {[} char \textbar{} \emph{\texttt{'lognormal'}} {]}
  - Prefix used in the names of the newly created databases.
\item
  \texttt{'std='} {[} \emph{\texttt{true}} \textbar{} \texttt{false} {]}
  - Compute the std deviations of the log-normal distributions.
\end{itemize}

\paragraph{Description}


