

    \filetitle{model}{Create new model object based on model file}{model/model}

	\paragraph{Syntax}

\begin{verbatim}
M = model(FName,...)
M = model(M,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{FName} {[} char \textbar{} cellstr {]} - Name(s) of model
  file(s) that will be loaded and converted to a new model object.
\item
  \texttt{M} {[} model {]} - Existing model object that will be rebuilt
  as if from a model file.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{M} {[} model {]} - New model object based on the input model
  code file or files.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'assign='} {[} struct \textbar{} \emph{empty} {]} - Assign
  model parameters and/or steady states from this database at the time
  the model objects is being created.
\item
  \texttt{'baseYear='} {[} numeric \textbar{} \emph{2000} {]} - Base
  year for constructing deterministic time trends.
\item
  \texttt{'blazer='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Perform block-recursive analysis of steady-state equations at
  the time the model object is being created; the option works only in
  nonlinear models.
\item
  \texttt{'comment='} {[} char \textbar{} \emph{empty} {]} - Text
  comment attached to the model object.
\item
  \texttt{'declareParameters='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - If \texttt{false}, skip parameter declaration in
  the model file, and determine the list of parameters automatically as
  names found in equations but not declared.
\item
  \texttt{'epsilon='} {[} numeric \textbar{} \emph{eps\^{}(1/4)} {]} -
  The minimum relative step size for numerical differentiation.
\item
  \texttt{'linear='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Indicate linear models.
\item
  \texttt{'makeBkw='} {[} \emph{\texttt{@auto}} \textbar{} \texttt{@all}
  \textbar{} cellstr \textbar{} char {]} - Variables included in the
  list will be made part of the vector of backward-looking variables;
  \texttt{@auto} means the variables that do not have any lag in model
  equations will be put in the vector of forward-looking variables.
\item
  \texttt{'multiple='} {[} true \textbar{} \emph{false} {]} - Allow each
  variable, shock, or parameter name to be declared (and assigned) more
  than once in the model file.
\item
  \texttt{'optimal='} {[} \texttt{'commitment'} \textbar{}
  \emph{\texttt{'discretion'}} {]} - Type of optimal policy calculated;
  only applies when the keyword \href{modellang/min}{\texttt{min}} is
  used in the model file.
\item
  \texttt{'removeLeads='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Remove all leads from the state-space
  vector, keep included only current dates and lags.
\item
  \texttt{'sstateOnly='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Read in only the steady-state versions of
  equations (if available).
\item
  \texttt{'std='} {[} numeric \textbar{} \texttt{@auto} {]} - Default
  standard deviation for model shocks; \texttt{@auto} means \texttt{1}
  for linear models and \texttt{log(1.01)} for nonlinear models.
\item
  \texttt{'userdata='} {[} \ldots{} \textbar{} \emph{empty} {]} - Attach
  user data to the model object.
\end{itemize}

\paragraph{Description}

\subparagraph{Loading a model file}

The \texttt{model} function can be used to read in a
\href{modellang/Contents}{model file} named \texttt{fname}, and create a
model object \texttt{m} based on the model file. You can then work with
the model object in your own m-files, using using the IRIS
\href{model/Contents}{model functions} and standard Matlab functions.

If \texttt{fname} is a cell array of more than one file names then all
files are combined together in order of appearance.

\subparagraph{Re-building an existing model
object}

The only instance where you may need to call a model function on an
existing model object is to change the \texttt{'removeLeads='} option.
Of course, you can always achieve the same by loading the original model
file.

\paragraph{Example}

Read in a model code file named \texttt{my.model}, and declare the model
as linear:

\begin{verbatim}
m = model('my.model','linear',true);
\end{verbatim}

\paragraph{Example}

Read in a model code file named \texttt{my.model}, declare the model as
linear, and assign some of the model parameters:

\begin{verbatim}
m = model('my.model','linear=',true,'assign=',P);
\end{verbatim}

Note that this is equivalent to

\begin{verbatim}
m = model('my.model','linear=',true);
m = assign(m,P);
\end{verbatim}

unless some of the parameters passed in to the \texttt{model} fuction
are needed to evaluate \href{modellang/if}{\texttt{if}} or
\href{modellang/switch}{\texttt{!switch}} expressions.


