

    \filetitle{set}{Change modifiable model object property}{model/set}

	\paragraph{Syntax}

\begin{verbatim}
M = set(M,Request,Value)
M = set(M,Request,Value,Request,Value,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{M} {[} model {]} - Model object.
\item
  \texttt{Request} {[} char {]} - Name of a modifiable model object
  property that will be changed.
\item
  \texttt{Value} {[} \ldots{} {]} - Value to which the property will be
  set.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{M} {[} model {]} - Model object with the requested property or
  properties modified.
\end{itemize}

\paragraph{Valid requests to model
objects}

\subparagraph{Equation labels and
aliases}

\begin{itemize}
\item
  \texttt{'yLabels='}, \texttt{'xLabels='}, \texttt{'dLabels='},
  \texttt{'lLabels='} {[} cellstr {]} - Change the labels attached to,
  respectively, measurement equations (\texttt{y}), transition equations
  (\texttt{x}), deterministic trends (\texttt{d}), and dynamic links
  (\texttt{d}).
\item
  \texttt{'labels='} {[} cell {]} - Change the labels attached to all
  equations; needs to be a cellstr matching the size of
  \texttt{get(M,'labels')}.
\item
  \texttt{'yeqtnAlias='}, \texttt{'xeqtnAlias='},
  \texttt{'deqtnAlias='}, \texttt{'leqtnAlias='} {[} cellstr {]} -
  Change the aliases of, respectively, measurement equations
  (\texttt{y}), transition equations (\texttt{x}), deterministic trends
  (\texttt{d}), and dynamic links (\texttt{d}).
\item
  \texttt{'eqtnAlias='} {[} cell {]} - Change the aliases of all
  equations; needs to be a cellstr matching the size of
  \texttt{get(M,'eqtnAlias')}.
\end{itemize}

\subparagraph{Descriptions and aliases of variables, shocks, and
parameters}

\begin{itemize}
\item
  \texttt{'yDescript='}, \texttt{'xDescript='}, \texttt{'eDescript='},
  \texttt{'pDescript='} {[} cellstr {]} - Change the descriptions of,
  respectively, measurement variables (\texttt{y}), transition variables
  (\texttt{x}), shocks (\texttt{e}), and exogenous variables
  (\texttt{g}).
\item
  \texttt{'descript='} {[} struct {]} - Change the descriptions of all
  variables, parameters, and shocks; needs to be a struct (database)
  with fields corresponding to model names.
\item
  \texttt{'yAlias='}, \texttt{'xAlias='}, \texttt{'eAlias='},
  \texttt{'pAlias='} {[} cellstr {]} - Change the aliases of,
  respectively, measurement variables (\texttt{y}), transition variables
  (\texttt{x}), shocks (\texttt{e}), and exogenous variables
  (\texttt{g}).
\item
  \texttt{'alias='} {[} struct {]} - Change the aliases of all
  variables, parameters, and shocks; needs to be a struct (database)
  with fields corresponding to model names.
\end{itemize}

\subparagraph{Other requests}

\begin{itemize}
\item
  \texttt{'nAlt='} {[} numeric {]} - Change the number of alternative
  parameterisations.
\item
  \texttt{'stdVec='} {[} numeric {]} - Change the whole vector of std
  deviations.
\item
  \texttt{'tOrigin='} {[} numeric {]} - Change the base year for
  computing deterministic time trends in measurement variables.
\item
  \texttt{'epsilon='} {[} numeric {]} - Change the relative
  differentiation step when computing Taylor expansion.
\end{itemize}


