

    \filetitle{sstate}{Compute steady state or balance-growth path of the model}{model/sstate}

	\paragraph{Syntax}

\begin{verbatim}
[M,Flag] = sstate(M,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{M} {[} model {]} - Parameterised model object.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{M} {[} model {]} - Model object with newly computed steady
  state assigned.
\item
  \texttt{Flag} {[} \texttt{true} \textbar{} \texttt{false} {]} - True
  for parameterizations where steady state has been found successfully.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'linear='} {[} \emph{\texttt{@auto}} \textbar{} \texttt{true}
  \textbar{} \texttt{false} {]} - Solve for steady state using a linear
  approach, i.e.~based on the first-order solution matrices and the
  vector of constants.
\item
  \texttt{'warning='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Display IRIS warning produced by this function.
\end{itemize}

\subparagraph{Options for non-linear
models}

\begin{itemize}
\item
  \texttt{'blocks='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Re-arrarnge steady-state equations in recursive blocks before
  computing steady state.
\item
  \texttt{'display='} {[} \emph{\texttt{'iter'}} \textbar{}
  \texttt{'final'} \textbar{} \texttt{'notify'} \textbar{}
  \texttt{'off'} {]} - Level of screen output, see Optim Tbx.
\item
  \texttt{'endogenise='} {[} cellstr \textbar{} char \textbar{}
  \emph{empty} {]} - List of parameters that will be endogenised when
  computing the steady state; the number of endogenised parameters must
  match the number of transtion variables exogenised in the
  \texttt{'exogenised='} option.
\item
  \texttt{'exogenise='} {[} cellstr \textbar{} char \textbar{}
  \emph{empty} {]} - List of transition variables that will be
  exogenised when computing the steady state; the number of exogenised
  variables must match the number of parameters exogenised in the
  \texttt{'exogenise='} option.
\item
  \texttt{'fix='} {[} cellstr \textbar{} \emph{empty} {]} - List of
  variables whose steady state will not be computed and kept fixed to
  the currently assigned values.
\item
  \texttt{'fixAllBut='} {[} cellstr \textbar{} \emph{empty} {]} -
  Inverse list of variables whose steady state will not be computed and
  kept fixed to the currently assigned values.
\item
  \texttt{'fixGrowth='} {[} cellstr \textbar{} \emph{empty} {]} - List
  of variables whose steady-state growth will not be computed and kept
  fixed to the currently assigned values.
\item
  \texttt{'fixGrowthAllBut='} {[} cellstr \textbar{} \emph{empty} {]} -
  Inverse list of variables whose steady-state growth will not be
  computed and kept fixed to the currently assigned values.
\item
  \texttt{'fixLevel='} {[} cellstr \textbar{} \emph{empty} {]} - List of
  variables whose steady-state levels will not be computed and kept
  fixed to the currently assigned values.
\item
  \texttt{'fixLevelAllBut='} {[} cellstr \textbar{} \emph{empty} {]} -
  Inverse list of variables whose steady-state levels will not be
  computed and kept fixed to the currently assigned values.
\item
  \texttt{'growth='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - If \texttt{true}, both the steady-state levels and growth rates
  will be computed; if \texttt{false}, only the levels will be computed
  assuming that the model is either stationary or that the correct
  steady-state growth rates are already assigned in the model object.
\item
  \texttt{'logMinus='} {[} cell \textbar{} char \textbar{} \emph{empty}
  {]} - List of log variables whose steady state will be restricted to
  negative values in this run of \texttt{sstate}.
\item
  \texttt{'optimSet='} {[} cell \textbar{} \emph{empty} {]} - Name-value
  pairs with Optim Tbx settings; see \texttt{help optimset} for details
  on these settings.
\item
  \texttt{'refresh='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Refresh dynamic links after steady state is computed.
\item
  \texttt{'reuse='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Reuse the steady-state values calculated for a parameterisation
  to initialise the next parameterisation.
\item
  \texttt{'solver='} {[} \texttt{'fsolve'} \textbar{}
  \emph{\texttt{'lsqnonlin'}} {]} - Solver function used to solve for
  the steady state of non-linear models; it can be either of the two
  Optimization Tbx functions, or a user-supplied solver.
\item
  \texttt{'sstate='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  \textbar{} cell {]} - If \texttt{true} or a cell array, the steady
  state is re-computed in each iteration; the cell array can be used to
  modify the default options with which the \texttt{sstate} function is
  called.
\item
  \texttt{'unlog='} {[} cell \textbar{} char \textbar{} \emph{empty} {]}
  - List of log variables that will be temporarily treated as non-log
  variables in this run of \texttt{sstate}, i.e.~their steady-state
  levels will not be restricted to either positive or negative values.
\end{itemize}

\subparagraph{Options for linear
models}

\begin{itemize}
\item
  \texttt{'refresh='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Refresh dynamic links before steady state is computed.
\item
  \texttt{'solve='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Solve model before computing steady state.
\end{itemize}

\paragraph{Description}

Note that for backward compatibility, the option \texttt{'growth='} is
set to \texttt{false} by default so that either the model is assumed
stationary or the steady-state growth rates have been already
pre-assigned to the model object. To use the \texttt{sstate} function
for computing both the steady-state levels and steady-state growth rates
in a balanced-growth model, you need to set the option
\texttt{'growth=' true}.

\paragraph{Example}


