

    \filetitle{arwm}{Adaptive random-walk Metropolis posterior simulator}{poster/arwm}

	\paragraph{Syntax}

\begin{verbatim}
[Theta,LogPost,ArVec,PosUpd] = arwm(Pos,NDraw,...)
[Theta,LogPost,ArVec,PosUpd,SgmVec,FinalCov] = arwm(Pos,NDraw,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{Pos} {[} poster {]} - Initialised posterior simulator object.
\item
  \texttt{NDraw} {[} numeric {]} - Length of the chain not including
  burn-in.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{Theta} {[} numeric {]} - MCMC chain with individual parameters
  in rows.
\item
  \texttt{LogPost} {[} numeric {]} - Vector of log posterior density (up
  to a constant) in each draw.
\item
  \texttt{ArVec} {[} numeric {]} - Vector of cumulative acceptance
  ratios.
\item
  \texttt{PosUpd} {[} poster {]} - Posterior simulator object with its
  properties updated so to capture the final state of the simulation.
\item
  \texttt{SgmVec} {[} numeric {]} - Vector of proposal scale factors in
  each draw.
\item
  \texttt{FinalCov} {[} numeric {]} - Final proposal covariance matrix;
  the final covariance matrix of the random walk step is
  Scale(end)\^{}2*FinalCov.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'adaptProposalCov='} {[} numeric \textbar{}
  \emph{\texttt{0.5}} {]} - Speed of adaptation of the Cholesky factor
  of the proposal covariance matrix towards the target acceptanace
  ratio, \texttt{targetAR}; zero means no adaptation.
\item
  \texttt{'adaptScale='} {[} numeric \textbar{} \emph{\texttt{1}} {]} -
  Speed of adaptation of the scale factor to deviations of acceptance
  ratios from the target ratio, \texttt{targetAR}.
\item
  \texttt{'burnin='} {[} numeric \textbar{} \emph{\texttt{0.10}} {]} -
  Number of burn-in draws entered either as a percentage of total draws
  (between 0 and 1) or directly as a number (integer greater that one).
  Burn-in draws will be added to the requested number of draws
  \texttt{ndraw} and discarded after the posterior simulation.
\item
  \texttt{'estTime='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Display and update the estimated time to go in the command
  window.
\item
  \texttt{'firstPrefetch='} {[} numeric \textbar{} \emph{\texttt{Inf}}
  {]} - First draw where parallelised pre-fetching will be used;
  \texttt{Inf} means no pre-fetching.
\item
  \texttt{'gamma='} {[} numeric \textbar{} \emph{\texttt{0.8}} {]} - The
  rate of decay at which the scale and/or the proposal covariance will
  be adapted with each new draw.
\item
  \texttt{'initScale='} {[} numeric \textbar{} \texttt{1/3} {]} -
  Initial scale factor by which the initial proposal covariance will be
  multiplied; the initial value will be adapted to achieve the target
  acceptance ratio.
\item
  \texttt{'lastAdapt='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
  Last point at which the proposal covariance will be adapted;
  \texttt{Inf} means adaptation will continue until the last draw. Can
  also be entered as a percentage of total draws (a number strictly
  between 0 and 1).
\item
  \texttt{'nStep='} {[} numeric \textbar{} *\texttt{1} {]} - Number of
  pre-fetched steps computed in parallel; only works with
  \texttt{firstPrefetch=} smaller than \texttt{NDraw}.
\item
  \texttt{'progress='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Display progress bar in the command
  window.
\item
  \texttt{'saveAs='} {[} char \textbar{} \emph{empty} {]} - File name
  where results will be saved when the option \texttt{'saveEvery='} is
  used.
\item
  \texttt{'saveEvery='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
  Every N draws will be saved to an HDF5 file, and removed from
  workspace immediately; no values will be returned in the output
  arguments \texttt{Theta}, \texttt{LogPost}, \texttt{AR},
  \texttt{Scale}; the option \texttt{'saveAs='} must be used to specify
  the file name; \texttt{Inf} means a normal run with no saving.
\item
  \texttt{'targetAR='} {[} numeric \textbar{} \emph{\texttt{0.234}} {]}
  - Target acceptance ratio.
\end{itemize}

\paragraph{Description}

The function \texttt{poster/arwm} returns the simulated chain of
parameters and the corresponding value of the log posterior density. To
obtain simulated sample statistics for each parameter (such as posterior
mean, median, percentiles, etc.) use the function
\href{poster/stats}{\texttt{poster/stats}} to process the simulated
chain and calculate the statistics.

The properties of the posterior object returned as the 4th output
argument are updated so that they capture the final state of the
posterior simulations. This can be used to initialize a next simulation
at the point where the previous ended.

\subparagraph{Parallelised ARWM}

Set \texttt{'nStep='} greater than \texttt{1}, and
\texttt{'firstPrefetch='} smaller than \texttt{NDraw} to start a
pre-fetching parallelised algorithm (pre-fetched will be all draws
starting from \texttt{'firstPrefetch='}); to that end, a pool of
parallel workers (using e.g. \texttt{matlabpool} from the Parallel
Computing Toolbox) must be opened before calling \texttt{arwm}.

With pre-fetching, all possible paths \texttt{'nStep='} steps ahead
(i.e.~all possible combinations of reject/accept) are pre-evaluated in
parallel, and then the resulting path is selected. Adapation then occurs
only every \texttt{'nStep='} steps, and hence the results will always
somewhat differ from a serial run. Identical results can be obtained by
turning down adaptation before pre-fetching starts, i.e.~by setting
\texttt{'lastAdapt='} smaller than \texttt{'firstPrefetch='} (and,
obviously, by re-setting the random number generator).

\paragraph{References}

\begin{itemize}
\item
  Brockwell, A.E., 2005. ``Parallel Markov Chain Monte Carlo Simulation
  by Pre-Fetching,'' CMU Statistics Dept. Tech. Report 802.
\item
  Strid, I., 2009. ``Efficient parallelisation of Metropolis-Hastings
  algorithms using a prefetching approach,'' SSE/EFI Working Paper
  Series in Economics and Finance No. 706.
\end{itemize}

\paragraph{Example}


