
    \foldertitle{VAR}{Vector Autoregressions (VAR Objects)}{VAR/Contents}

	VAR objects can be constructed as plain VARs or simple panel VARs (with
fixed effect), and estimated without or with prior dummy observations
(quasi-bayesian VARs). VAR objects are reduced-form models; they are
also the point of departure for identifying structural VARs
(\href{SVAR/Contents}{\texttt{SVAR}} objects).

VAR methods:

\paragraph{Constructor}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{VAR/VAR}{\texttt{VAR}} - Create new empty reduced-form VAR
  object.
\end{itemize}

\paragraph{Getting information about VAR
objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{VAR/addparam}{\texttt{addparam}} - Add VAR parameters to a
  database (struct).
\item
  \href{VAR/comment}{\texttt{comment}} - Get or set user comments in an
  IRIS object.
\item
  \href{VAR/companion}{\texttt{companion}} - Matrices of first-order
  companion VAR.
\item
  \href{VAR/eig}{\texttt{eig}} - Eigenvalues of a VAR process.
\item
  \href{VAR/fprintf}{\texttt{fprintf}} - Write VAR model as formatted
  model code to text file.
\item
  \href{VAR/get}{\texttt{get}} - Query VAR object properties.
\item
  \href{VAR/iscompatible}{\texttt{iscompatible}} - True if two VAR
  objects can occur together on the LHS and RHS in an assignment.
\item
  \href{VAR/isexplosive}{\texttt{isexplosive}} - True if any eigenvalue
  is outside unit circle.
\item
  \href{VAR/ispanel}{\texttt{ispanel}} - True for panel VAR objects.
\item
  \href{VAR/isstationary}{\texttt{isstationary}} - True if all
  eigenvalues are within unit circle.
\item
  \href{VAR/length}{\texttt{length}} - Number of alternative
  parameterisations in VAR object.
\item
  \href{VAR/mean}{\texttt{mean}} - Mean of VAR process.
\item
  \href{VAR/nfitted}{\texttt{nfitted}} - Number of data points fitted in
  VAR estimation.
\item
  \href{VAR/rngcmp}{\texttt{rngcmp}} - True if two VAR objects have been
  estimated using the same dates.
\item
  \href{VAR/sprintf}{\texttt{sprintf}} - Print VAR model as formatted
  model code.
\item
  \href{VAR/sspace}{\texttt{sspace}} - Quasi-triangular state-space
  representation of VAR.
\item
  \href{VAR/userdata}{\texttt{userdata}} - Get or set user data in an
  IRIS object.
\end{itemize}

\paragraph{Referencing VAR objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{VAR/group}{\texttt{group}} - Retrieve VAR object from panel VAR
  for specified group of data.
\item
  \href{VAR/subsasgn}{\texttt{subsasgn}} - Subscripted assignment for
  VAR objects.
\item
  \href{VAR/subsref}{\texttt{subsref}} - Subscripted reference for VAR
  objects.
\end{itemize}

\paragraph{Simulation, forecasting and
filtering}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{VAR/ferf}{\texttt{ferf}} - Forecast error response function.
\item
  \href{VAR/filter}{\texttt{filter}} - Filter data using a VAR model.
\item
  \href{VAR/forecast}{\texttt{forecast}} - Unconditional or conditional
  VAR forecasts.
\item
  \href{VAR/instrument}{\texttt{instrument}} - Define forecast
  conditioning instruments in VAR models.
\item
  \href{VAR/resample}{\texttt{resample}} - Resample from a VAR object.
\item
  \href{VAR/simulate}{\texttt{simulate}} - Simulate VAR model.
\end{itemize}

\paragraph{Manipulating VARs}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{VAR/assign}{\texttt{assign}} - Manually assign system matrices
  to VAR object.
\item
  \href{VAR/alter}{\texttt{alter}} - Expand or reduce the number of
  alternative parameterisations within a VAR object.
\item
  \href{VAR/backward}{\texttt{backward}} - Backward VAR process.
\item
  \href{VAR/demean}{\texttt{demean}} - Remove constant and the effect of
  exogenous inputs from VAR object.
\item
  \href{VAR/horzcat}{\texttt{horzcat}} - Combine two compatible VAR
  objects in one object with multiple parameterisations.
\item
  \href{VAR/integrate}{\texttt{integrate}} - Integrate VAR process and
  data associated with it.
\item
  \href{VAR/xasymptote}{\texttt{xasymptote}} - Set or get asymptotic
  assumptions for exogenous inputs.
\end{itemize}

\paragraph{Stochastic properties}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{VAR/acf}{\texttt{acf}} - Autocovariance and autocorrelation
  functions for VAR variables.
\item
  \href{VAR/fmse}{\texttt{fmse}} - Forecast mean square error matrices.
\item
  \href{VAR/vma}{\texttt{vma}} - Matrices describing the VMA
  representation of a VAR process.
\item
  \href{VAR/xsf}{\texttt{xsf}} - Power spectrum and spectral density
  functions for VAR variables.
\end{itemize}

\paragraph{Estimation, identification, and statistical
tests}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{VAR/estimate}{\texttt{estimate}} - Estimate a reduced-form VAR
  or BVAR.
\item
  \href{VAR/infocrit}{\texttt{infocrit}} - Populate information criteria
  for a parameterised VAR.
\item
  \href{VAR/lrtest}{\texttt{lrtest}} - Likelihood ratio test for VAR
  models.
\item
  \href{VAR/portest}{\texttt{portest}} - Portmanteau test for
  autocorrelation in VAR residuals.
\item
  \href{VAR/schur}{\texttt{schur}} - Compute and store triangular
  representation of VAR.
\end{itemize}

\paragraph{Getting on-line help on VAR
functions}

\begin{verbatim}
help VAR
help VAR/function_name
\end{verbatim}



