

    \filetitle{get}{Query VAR object properties}{VAR/get}

	\paragraph{Syntax}

\begin{verbatim}
Ans = get(V,Query)
[Ans,Ans,...] = get(V,Query,Query,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{V} {[} VAR {]} - VAR object.
\item
  \texttt{Query} {[} char {]} - Query to the VAR object.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{Ans} {[} \ldots{} {]} - Answer to the query.
\end{itemize}

\paragraph{Valid queries to VAR
objects}

\subparagraph{VAR variables}

\begin{itemize}
\item
  \texttt{'yList'} -- Returns {[} cellstr {]} the names of endogenous
  variables.
\item
  \texttt{'eList'} -- Returns {[} cellstr {]} the names of residuals or
  shocks.
\item
  \texttt{'iList'} -- Returns {[} cellstr {]} the names of conditioning
  (forecast) instruments.
\item
  \texttt{'ny'} -- Returns {[} numeric {]} the number of variables.
\item
  \texttt{'ne'} -- Returns {[} numeric {]} the number of residuals or
  shocks.
\item
  \texttt{'ni'} -- Returns {[} numeric {]} the number of conditioning
  (forecast) instruments.
\end{itemize}

\subparagraph{System matrices}

\begin{itemize}
\item
  \texttt{'A\#'}, \texttt{'A*'}, \texttt{'A\$'} -- Returns {[} numeric
  {]} the transition matrix in one of the three possible forms; see
  Description.
\item
  \texttt{'K'}, \texttt{'const'} -- Returns {[} numeric {]} the constant
  vector or matrix (the latter for panel VARs).
\item
  \texttt{'J'} -- Returns {[} numeric {]} the coefficient matrix in
  front of exogenous inputs.
\item
  \texttt{'Omg'}, \texttt{'Omega'} -- Returns {[} numeric {]} the
  covariance matrix of one-step-ahead forecast errors, i.e.~reduced-form
  residuals. Note that this query returns the same matrix also for
  structural VAR (SVAR) objects.
\item
  \texttt{'Sgm'}, \texttt{'Sigma'} -- Returns {[} numeric {]} the
  covariance matrix of the VAR parameter estimates; the matrix is
  non-empty only if the option \texttt{'covParam='} has been set to
  \texttt{true} at estimation time.
\item
  \texttt{'G'} -- Returns {[} numeric {]} the coefficient matrix on
  cointegration terms.
\end{itemize}

\subparagraph{Information criteria}

\begin{itemize}
\item
  \texttt{'AIC'} -- Returns {[} numeric {]} Akaike information
  criterion.
\item
  \texttt{'SBC'} -- Returns {[} numeric {]} Schwarz bayesian criterion.
\end{itemize}

\subparagraph{Other queries}

\begin{itemize}
\item
  \texttt{'cumLong'} -- Returns {[} numeric {]} the matrix of long-run
  cumulative responses.
\item
  \texttt{'nFree'} -- Returns {[} numeric {]} the number of freely
  estimated (hyper-) parameters.
\item
  \texttt{'order'}, \texttt{'p'} -- Returns {[} numeric {]} the order of
  the VAR object.
\end{itemize}

\paragraph{Description}

\subparagraph{Transition matrix}

There are three queries to request the VAR transition matrix:
\texttt{'A\#'}, \texttt{'A*'}, \texttt{'A\$'}. They differ in how the
higher-order transition matrices are arranged.

\begin{itemize}
\item
  \texttt{'A\#'} returns \texttt{cat(3,I,-A1,...,-Ap)} where \texttt{I}
  is an identity matrix, and \texttt{A1}, \ldots{} \texttt{Ap} are the
  coefficient matrices on individual lags.
\item
  \texttt{'A\#'} returns \texttt{cat(3,A1,...,Ap)} where \texttt{A1},
  \ldots{} \texttt{Ap} are the coefficient matrices on individual lags.
\item
  \texttt{'A\$'} returns \texttt{{[}A1,...,Ap{]}} where \texttt{A1},
  \ldots{} \texttt{Ap} are the coefficient matrices on individual lags.
\end{itemize}

\paragraph{Example}


