

    \filetitle{simulate}{Simulate VAR model}{VAR/simulate}

	\paragraph{Syntax}

\begin{verbatim}
Outp = simulate(V,Inp,Range,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{V} {[} VAR {]} - VAR object that will be simulated.
\item
  \texttt{Inp} {[} tseries \textbar{} struct {]} - Input data from which
  the initial condtions and residuals will be taken.
\item
  \texttt{Range} {[} numeric {]} - Simulation range; must not refer to
  \texttt{Inf}.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{Outp} {[} tseries {]} - Simulated output data.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'contributions='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Decompose the simulated paths into the
  contributions of individual residuals, initial condition, the
  constant, and exogenous inputs; see Description.
\item
  \texttt{'deviation='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Treat input and output data as deviations
  from unconditional mean.
\item
  \texttt{'output='} {[} \emph{\texttt{'auto'}} \textbar{}
  \texttt{'dbase'} \textbar{} \texttt{'tseries'} {]} - Format of output
  data.
\end{itemize}

\paragraph{Description}

\subparagraph{Backward simulation
(backcast)}

If the \texttt{Range} is a vector of decreasing dates, the simulation is
performed backward. The VAR object is first converted to its backward
representation using the function
\href{VAR/backward}{\texttt{backward}}, and then the data are simulated
from the latest date to the earliest date.

\subparagraph{Simulation of
contributions}

With the option \texttt{'contributions=' true}, the output database
contains Ne+2 columns for each variable, where Ne is the number of
residuals. The first Ne columns are the contributions of the individual
shocks, the (Ne+1)-th column is the contribution of initial condition
and the constant, and the last, (Ne+2)-th columns is the contribution of
exogenous inputs.

Contribution simulations can be only run on VAR objects with one
parameterization.

\paragraph{Example}


