

    \filetitle{sprintf}{Print VAR model as formatted model code}{VAR/sprintf}

	\paragraph{Syntax}

\begin{verbatim}
[C,D] = sprintf(V,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{V} {[} VAR {]} - VAR object that will be printed as a
  formatted model code.
\item
  Output arguments
\item
  \texttt{C} {[} cellstr {]} - Text string with the model code for each
  parameterisation.
\item
  \texttt{D} {[} cell {]} - Parameter database for each
  parameterisation; if \texttt{'hardParameters='} is true, the databases
  will be empty.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'decimal='} {[} numeric \textbar{} \emph{empty} {]} -
  Precision (number of decimals) at which the coefficients will be
  written if \texttt{'hardParameters='} is true; if empty, the
  \texttt{'format='} options is used.
\item
  \texttt{'declare='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Add declaration blocks and keywords for VAR variables, shocks,
  and equations.
\item
  \texttt{'eNames='} {[} cellstr \textbar{} char \textbar{} \emph{empty}
  {]} - Names that will be given to the VAR residuals; if empty, the
  names from the VAR object will be used.
\item
  \texttt{'format='} {[} char \textbar{} \emph{`\%+.16g'} {]} - Numeric
  format for parameter values; it will be used only if
  \texttt{'decimal='} is empty.
\item
  \texttt{'hardParameters='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Print coefficients as hard numbers; otherwise,
  create parameter names and return a parameter database.
\item
  \texttt{'yNames='} {[} cellstr \textbar{} char \textbar{} \emph{empty}
  {]} - Names that will be given to the variables; if empty, the names
  from the VAR object will be used.
\item
  \texttt{'tolerance='} {[} numeric \textbar{} \emph{getrealsmall()} {]}
  - Treat VAR coefficients smaller than \texttt{'tolerance='} in
  absolute value as zeros; zero coefficients will be dropped from the
  model code.
\end{itemize}

\paragraph{Description}

\paragraph{Example}


