

    \filetitle{xsf}{Power spectrum and spectral density functions for VAR variables}{VAR/xsf}

	\paragraph{Syntax}

\begin{verbatim}
[S,D] = xsf(V,Freq,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{V} {[} VAR {]} - VAR object.
\item
  \texttt{Freq} {[} numeric {]} - Vector of Frequencies at which the
  XSFs will be evaluated.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{S} {[} numeric {]} - Power spectrum matrices.
\item
  \texttt{D} {[} numeric {]} - Spectral density matrices.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'applyTo='} {[} cellstr \textbar{} char \textbar{}
  \emph{\texttt{@all}} {]} - List of variables to which the
  \texttt{'filter='} will be applied; \texttt{@all} means all variables.
\item
  \texttt{'filter='} {[} char \textbar{} \emph{empty} {]} - Linear
  filter that is applied to variables specified by `applyto'.
\item
  \texttt{'nFreq='} {[} numeric \textbar{} \emph{256} {]} - Number of
  equally spaced frequencies over which the `filter' is numerically
  integrated.
\item
  \texttt{'progress='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Display progress bar in the command
  window.
\end{itemize}

\paragraph{Description}

The output matrices, \texttt{S} and \texttt{D}, are
\texttt{N}-by-\texttt{N}-by-\texttt{K}, where \texttt{N} is the number
of VAR variables and \texttt{K} is the number of frequencies (i.e.~the
length of the vector \texttt{freq}).

The k-th page is the \texttt{S} matrix, i.e. \texttt{S(:,:,k)}, is the
cross-spectrum matrix for the VAR variables at the k-th frequency.
Similarly, the \texttt{k}-th page in \texttt{D}, i.e. \texttt{D(:,:,k)},
is the cross-density matrix.

\paragraph{Example}


