

    \filetitle{!if...!elseif...!else...!end}{Choose block of code based on logical condition}{modellang/if}

	\paragraph{Syntax with else and elseif
clauses}

\begin{verbatim}
!if Condition1
    Block1
!elseif Condition2
    Block2
!elseif Condition3
...
!else
    Block3
!end
\end{verbatim}

\paragraph{Syntax with an else clause
only}

\begin{verbatim}
!if Condition1
    Block1
!else
    Block2
!end
\end{verbatim}

\paragraph{Syntax without an else
clause}

\begin{verbatim}
!if Condition
    Block1
!end
\end{verbatim}

\paragraph{Description}

The \texttt{!if...!elseif...!else...!end} command works the same way as
its counterpart in the Matlab programming language.

Use the \texttt{!if...!else...!end} command to create branches or
versions of the model code. Whether a block of code in a particular
branch is used or discarded, depends on the condition after the opening
\texttt{!if} command and the conditions after subsequent
\texttt{!elseif} commands if present. The condition must be a Matlab
expression that evaluates to true or false. The condition can refer to
model parameters, or to other fields included in the database passed in
through the option `\texttt{assign=}' in the
\href{model/model}{\texttt{model}} function.

\paragraph{Example}

\begin{verbatim}
!if B < Inf
    % This is a linearised sticky-price Phillips curve.
    pi = A*pi{-1} + (1-A)*pi{1} + B*log(mu*rmc);
!else
    % This is a flexible-price mark-up rule.
    rmc = 1/mu;
!end
\end{verbatim}

If you set the parameter \texttt{B} to Inf in the parameter database
when reading in the model file, then the flexible-price equatio,
\texttt{rmc = 0}, is used and the Phillips curve equation discarded. To
use the Phillips curve equation instead, you need to re-read the model
file with \texttt{B} set to a number other than Inf. In this example,
\texttt{B} needs to be, obviously, declared as a model parameter.

\paragraph{Example}

\begin{verbatim}
!if exogenous == true
    x = y;
!else
    x = rho*x{-1} + epsilon;
!end
\end{verbatim}

When reading the model file in, create a parameter database, include at
least a field named \texttt{exogenous} in it, and use the
\texttt{'assign='} option to pass the database in. Note that you do not
need to declare \texttt{exogenous} as a parameter in the model file.

\begin{verbatim}
P = struct();
P.exogenous = true;
...
m = model('my.model','assign=',P);
\end{verbatim}

In this case, the model will contain the first equation,
\texttt{x = rho*x\{-1\} + epsilon;} will be used, and the other
discarded. To use the other equation, \texttt{x = y}, you need to
re-read the model file with \texttt{exogenous} set to false:

\begin{verbatim}
P = struct();
P.exogenous = false;
...
m = model('my.model','assign=',P);
\end{verbatim}

You can also use an abbreviate syntax to assign control parameters when
readin the model file; for instance

\begin{verbatim}
m = model('my.model','exogenous=',true);
\end{verbatim}


