

    \filetitle{!log\_variables}{List of log-linearised variables}{modellang/logvariables}

	\paragraph{Syntax}

\begin{verbatim}
!log_variables
    VariableName, VariableName, 
    VariableName, ...
\end{verbatim}

\paragraph{Syntax with inverted list}

\begin{verbatim}
!log_variables
    !all_but
    VariableName, VariableName, 
    VariableName, ...
\end{verbatim}

\paragraph{Syntax with regular
expression(s)}

\begin{verbatim}
!log_variables
    VariableName, VariableName, 
    VariableName, ...
    <REGEXP>, <REGEXP>, ...
\end{verbatim}

\paragraph{Description}

List all log variables under this headings. Only measurement or
transition variables can be declared as log variables.

In non-linear models, all variables are linearised around the steady
state or a balanced-growth path. If you wish to log-linearise some of
them instead, put them on a \texttt{!log\_variables} list. You can also
use the \texttt{!all\_but} keyword to indicate an inverse list: all
variables will be log-linearised except those listed.

To create the list of log variables, you can also use regular
expressions, each enlosed in a pair of angle brackets,
\texttt{\textless{}} and \texttt{\textgreater{}}. All measurement and
transition variables whose names match one of the regular expressions
will be declared as log variables. See also help on regular expressions
in the Matlab documentation.

\paragraph{Example}

The following block of code will cause the variables \texttt{Y},
\texttt{C}, \texttt{I}, and \texttt{K} to be declared as log variables,
and hence log-linearised in the model solution, while \texttt{r} and
\texttt{pie} will be linearised:

\begin{verbatim}
!transition_variables
    Y, C, I, K, r, pie

!log_variables
    Y, C, I, K
\end{verbatim}

You can do the same job by writing

\begin{verbatim}
!transition_variables
    Y, C, I, K, r, pie

!log_variables
    !all_but
    r, pie
\end{verbatim}

\paragraph{Example}

We again achieve the same result as above, but now using a regular
expression.

\begin{verbatim}
!transition_variables
    Y, C, I, K, r, pie

!log_variables
    <[A-Z]\w*>
\end{verbatim}

The regular expression \texttt{{[}A-Z{]}\textbackslash{}w*} selects all
variables whose names start with an upper-case letter. Hence, again the
variables \texttt{Y}, \texttt{C}, \texttt{I}, and \texttt{K} will be
declared as log variables.


