

    \filetitle{!substitutions}{Define text substitutions}{modellang/substitutions}

	\paragraph{Syntax}

\begin{verbatim}
!substitutions
    SubsName := TextString;
    SubsName := TextString;
    ...
\end{verbatim}

\paragraph{Description}

The \texttt{!substitutions} starts a block with substitution
definitions. The definition of each substitution must begin with the
name of the substitution, followed by a colon-equal sign, \texttt{:=},
and a text string ended with a semi-colon. The semi-colon is not part of
the substitution.

The substitutions can be used in any of the model equations, i.e.~in
\href{modellang/transitionequations}{transition equations},
\href{modellang/measurementequations}{measurement equations},
\href{modellang/dtrends}{deterministic trend equations}, and
\href{modellang/links}{dynamic links}. Each occurence of the name of a
substitution enclosed in dollar signs, i.e.
\texttt{\$substitution\_name\$}, in model equations will be replaced
with the text string from the substitution's definition.

Substitutions can also refer to other substitutions; make sure, though,
that they are not recursive. Also, remember to parenthesise the
definitions of the substitutions (or the references to them) in the
equations properly so that the resulting mathematical expressions are
evaluated properly.

\paragraph{Example}

\begin{verbatim}
!substitution
    a := ((omega1+omega2)/(omega1+omega2+omega3));

!transition_equations
    X = $a$^2*Y + (1-$a$^2)*Z;
\end{verbatim}

In this example, we assume that \texttt{omega1}, \texttt{omega2}, and
\texttt{omega3} are declared as parameters. The equation will expand to

\begin{verbatim}
    X = ((omega1+omega2)/(omega1+omega2+omega3))^2*Y + ...
      (1-((omega1+omega2)/(omega1+omega2+omega3))^2)*Z;
\end{verbatim}

Note that if had not used the outermost parentheses in the definition of
the substitution, the resulting expression would not have given us what
we meant: The square operator would have only applied to the
denominator.


