
    \foldertitle{plan}{Model Simulation Plans (plan Objects)}{plan/Contents}

	Simulation plans complement the use of the
\href{model/simulate}{\texttt{model/simulate}} or
\href{model/jforecast}{\texttt{model/jforecast}} functions.

You need to use a simulation plan object to set up the following types
of more complex simulations or forecasts (or a combination of these):

\paragraph{simulations or forecasts with some of the model variables
temporarily}

exogenised;

\paragraph{simulations with some of the non-linear equations solved in
an
exact}

non-linear mode;

\paragraph{forecasts conditioned upon some
variables;}

The plan object is passed to the
\href{model/simulate}{\texttt{model/simulate}} or
\href{model/jforecast}{\texttt{model/jforecast}} functions through the
\texttt{'plan='} option.

Plan methods:

\paragraph{Constructor}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{plan/plan}{\texttt{plan}} - Create new empty simulation plan
  object.
\end{itemize}

\paragraph{Getting information about simulation
plans}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{plan/detail}{\texttt{detail}} - Display details of a simulation
  plan.
\item
  \href{plan/get}{\texttt{get}} - Query to plan object.
\item
  \href{plan/nnzcond}{\texttt{nnzcond}} - Number of conditioning data
  points.
\item
  \href{plan/nnzendog}{\texttt{nnzendog}} - Number of endogenised data
  points.
\item
  \href{plan/nnzexog}{\texttt{nnzexog}} - Number of exogenised data
  points.
\item
  \href{plan/nnznonlin}{\texttt{nnznonlin}} - Number of non-linearised
  data points.
\end{itemize}

\paragraph{Setting up simulation
plans}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{plan/autoexogenise}{\texttt{autoexogenise}} - Exogenise
  variables and automatically endogenise corresponding shocks.
\item
  \href{plan/condition}{\texttt{condition}} - Condition forecast upon
  the specified variables at the specified dates.
\item
  \href{plan/endogenise}{\texttt{endogenise}} - Endogenise shocks or
  re-endogenise variables at the specified dates.
\item
  \href{plan/exogenise}{\texttt{exogenise}} - Exogenise variables or
  re-exogenise shocks at the specified dates.
\item
  \href{plan/swap}{\texttt{swap}} - Swap endogeneity and exogeneity of
  variables and shocks.
\end{itemize}

\paragraph{Referencing plan objects}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{plan/subsref}{\texttt{subsref}} - Subscripted reference for plan
  objects.
\end{itemize}

\paragraph{Getting on-line help on simulation
plans}

\begin{verbatim}
help plan
help plan/function_name
\end{verbatim}



