

    \filetitle{align}{Vertically align the following K objects}{report/align}

	\paragraph{Syntax}

\begin{verbatim}
P.align(Caption,K,NCol,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{P} {[} struct {]} - Report object created by the
  \href{report/new}{\texttt{report.new}} function.
\item
  \texttt{Caption} {[} char {]} - Caption displayed only when describing
  the structure of the report on the screen, but not in the actual PDF
  report.
\item
  \texttt{K} {[} numeric {]} - Number of objects following this
  \texttt{align} that will be vertically aligned.
\item
  \texttt{NCol} {[} numeric {]} - Number of columns in which the objects
  will vertically aligned.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'hspace='} {[} numeric \textbar{} \emph{\texttt{2}} {]} -
  Horizontal space (in em units) inserted between two neighbouring
  objects.
\item
  \texttt{'separator='} {[} char \textbar{}
  \emph{\texttt{'\textbackslash{}medskip\textbackslash{}par'}} {]} -
  (Inheritable from parent objects) \LaTeX~commands that will be
  inserted after the aligned objects.
\item
  \texttt{'shareCaption='} {[} \emph{\texttt{'auto'}} \textbar{} true
  \textbar{} false {]} - (Inheritable from parent objects) Place a
  shared caption (title and subtitle) over each row of objects; the
  title of the first object in each row is used; \texttt{'auto'} means
  that the caption will be shared if they are identical for all objects
  in a row.
\item
  \texttt{'typeface='} {[} char \textbar{} \emph{empty} {]} - (Not
  inheritable from parent objects) \LaTeX~code specifying the typeface
  for the align element as a whole; it must use the declarative forms
  (such as \texttt{\textbackslash{}itshape}) and not the command forms
  (such as \texttt{\textbackslash{}textit\{...\}}).
\end{itemize}

\paragraph{Description}

Vertically aligned can be the following types of objects:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{report/figure}{\texttt{figure}}
\item
  \href{report/table}{\texttt{table}}
\item
  \href{report/matrix}{\texttt{matrix}}
\item
  \href{report/array}{\texttt{array}}
\end{itemize}

Note that the \texttt{align} object itself has no caption (even if you
specify one it will not be used). Only the objects within \texttt{align}
will be given captions. If the objects aligned on one row have identical
captions (i.e.~both titles and subtitles), only one caption will be
displayed centred above the objects.

Because \href{report/empty}{\texttt{empty}} objects count in the total
number of objects inluded in \texttt{align}, you can use
\href{report/empty}{\texttt{empty}} in to create blank space in a
particular position.

\paragraph{Example}


