

    \filetitle{band}{Add new data with lower and upper bounds to graph or table}{report/band}

	\paragraph{Syntax}

\begin{verbatim}
P.band(Caption,X,Low,High,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{P} {[} struct {]} - Report object created by the
  \href{report/new}{\texttt{report.new}} function.
\item
  \texttt{Caption} {[} char {]} - Caption used as a default legend entry
  in a graph, or in the leading column in a table.
\item
  \texttt{X} {[} tseries {]} - Input data with the centre of the band.
\item
  \texttt{Low} {[} tseries {]} - Input data with lower bounds; can be
  specified either relative to the centre or absolute, see the option
  \texttt{'relative='}.
\item
  \texttt{High} {[} tseries {]} - Input data with upper bounds; can be
  specified either relative to the centre or absolute, see the option
  \texttt{'relative='}.
\end{itemize}

\paragraph{Options for table and graph
bands}

\begin{itemize}
\item
  \texttt{'low='} {[} char \textbar{} \emph{`Low'} {]} - (Inheritable
  from parent objects) Mark used to denote the lower bound.
\item
  \texttt{'high='} {[} char \textbar{} \emph{`High'} {]} - (Inheritable
  from parent objects) Mark used to denote the upper bound.
\item
  \texttt{'relative='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - (Inheritable from parent objects) If true, the
  data for the lower and upper bounds are relative to the centre,
  i.e.~the bounds will be added to the centre (in this case,
  \texttt{LOW} must be negative numbers and \texttt{HIGH} must be
  positive numbers). If false, the bounds are absolute data (in this
  case \texttt{LOW} must be lower than \texttt{X}, and \texttt{HIGH}
  must be higher than \texttt{X}).
\end{itemize}

\paragraph{Options for table bands}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{'bandTypeface='} {[} char \textbar{}
  \emph{\texttt{'\textbackslash{}footnotesize'}} {]} - (Inheritable from
  parent objects) LaTeX format string used to typeset the lower and
  upper bounds.\%
\end{itemize}

\paragraph{Options for graph bands}

\begin{itemize}
\item
  \texttt{'plotType='} {[} \texttt{'errorbar'} \textbar{}
  \emph{\texttt{'patch'}} {]} - Type of plot used to draw the band.
\item
  \texttt{'relative='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - (Inheritable from parent objects) If true the
  lower and upper bounds will be, respectively, subtracted from and
  added to to the middle line.
\item
  \texttt{'white='} {[} numeric \textbar{} \emph{\texttt{0.85}} {]} -
  (Inheritable from parent objects) Proportion of white colour mixed
  with the center line color and used to fill the band area.
\end{itemize}

See help on \href{report/series}{\texttt{report/series}} for other
options available.

\paragraph{Generic options}

See help on \href{report/Contents}{generic options} in report objects.

\paragraph{Description}

\paragraph{Example}


