

    \filetitle{fanchart}{Add fanchart to graph}{report/fanchart}

	\paragraph{Syntax}

\begin{verbatim}
P.fanchart(Cap,X,Std,Prob,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{P} {[} struct {]} - Report object created by the
  \href{report/new}{\texttt{report.new}} function.
\item
  \texttt{Cap} {[} char {]} - Caption used as a legend entry for the
  line (mean of fanchart)
\item
  \texttt{X} {[} tseries {]} - Tseries object with input data to be
  displayed.
\item
  \texttt{Std} {[} tseries {]} - Tseries object with standard deviations
  of input data.
\item
  \texttt{Prob} {[} numeric {]} - Confidence porbabilities of intervals
  to be displayed.
\end{itemize}

\paragraph{Options for fancharts}

\begin{itemize}
\item
  \texttt{'asym='} {[} numeric \textbar{} tseries \textbar{}
  \emph{\texttt{1}} {]} - Ratio of asymmetry (area of upper part to one
  of lower part).
\item
  \texttt{'exclude='} {[} numeric \textbar{} true \textbar{}
  \emph{\texttt{false}} {]} - Exclude some of the confidence intervals.
\item
  \texttt{'factor='} {[} numeric \textbar{} \emph{\texttt{1}} {]} -
  factor to increase or decrease input standard deviations
\item
  \texttt{'fanLegend='} {[} cell \textbar{} \texttt{NaN} \textbar{}
  \emph{\texttt{Inf}} {]} - Legend entries used instead of confidence
  interval values; Inf means all confidence intervals values will be
  used to construct legend entries; NaN means the intervals will be
  exluded from legend; \texttt{NaN} in cellstr means the intervals of
  respective fancharts will be exluded from legend.
\end{itemize}

See help on \href{report/series}{\texttt{report/series}} for other
options available.

\paragraph{Description}

The confidence intervals are based on normal distributions with standard
deviations supplied by the user. Optionally, the user can also specify
assumptions about asymmetry and/or common correction factors.

\paragraph{Example}


