

    \filetitle{figure}{Start new figure}{report/figure}

	\paragraph{Syntax}

\begin{verbatim}
P.figure(Caption,...)
\end{verbatim}

\paragraph{Syntax to capture an existing figure
window}

This is an obsolete syntax, and will be removed from IRIS in a future
release. Use \href{report/userfigure}{\texttt{report/userfigure}}
instead.

\begin{verbatim}
P.figure(Caption,H,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{P} {[} struct {]} - Report object created by the
  \href{report/new}{\texttt{report.new}} function.
\item
  \texttt{Caption} {[} char \textbar{} cellstr {]} - Title or a cell
  array with title and subtitle displayed at the top of the figure; see
  Description for splitting the title or subtitle into multiple lines.
\item
  \texttt{H} {[} numeric {]} - See help on
  \href{report/userfigure}{\texttt{report/userfigure}}.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'aspectRatio='} {[} \texttt{@auto} \textbar{} numeric {]} -
  Plot box aspect ratio for all graphs in the figure; must be a 1-by-2
  vector describing the horizontal-to-vertical ratio.
\item
  \texttt{'captionTypeface='} {[} cellstr \textbar{} char \textbar{}
  \emph{\texttt{'\textbackslash{}large\textbackslash{}bfseries'}} {]} -
  LaTeX format commands for typesetting the figure caption; the
  subcaption format can be entered as the second cell in a cell array.
\item
  \texttt{'close='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - (Inheritable from parent objects) Close the underlying figure
  window when finished; see Description.
\item
  \texttt{'separator='} {[} char \textbar{}
  \emph{\texttt{'\textbackslash{}medskip\textbackslash{}par'}} {]} -
  (Inheritable from parent objects) LaTeX commands that will be inserted
  after the figure.
\item
  \texttt{'figureOptions='} {[} cell \textbar{} \emph{empty} {]} -
  Figure options that will be applied to the figure handle at opening.
\item
  \texttt{'figureScale='} {[} numeric \textbar{} \emph{\texttt{0.85}}
  {]} - (Inheritable from parent objects) Scale of the figure in the
  LaTeX document.
\item
  \texttt{'figureTrim='} {[} numeric \textbar{} \emph{\texttt{0}} {]} -
  Trim figure when it is inserted into the report by the specified
  amount of points; must be either a scalar or a 1-by-4 vector (points
  removed from left, bottom, right, top).
\item
  \texttt{'footnote='} {[} char \textbar{} \emph{empty} {]} - Footnote
  at the figure title; only shows if the title is non-empty.
\item
  \texttt{'sideways='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - (Inheritable from parent objects) Print
  the table rotated by 90 degrees.
\item
  \texttt{'style='} {[} struct \textbar{} \emph{empty} {]} - Apply this
  cascading style structure to the figure; see
  \href{qreport/qstyle}{\texttt{qstyle}}.
\item
  \texttt{'subplot='} {[} numeric \textbar{} \emph{\texttt{'auto'}} {]}
  - (Inheritable from parent objects) Subplot division of the figure.
\item
  \texttt{'typeface='} {[} char \textbar{} \emph{empty} {]} - (Not
  inheritable from parent objects) LaTeX code specifying the typeface
  for the figure as a whole; it must use the declarative forms (such as
  \texttt{\textbackslash{}itshape}) and not the command forms (such as
  \texttt{\textbackslash{}textit\{...\}}).
\item
  \texttt{'visible='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - (Inheritable from parent objects) Visibility of the underlying
  Matlab figure window.
\end{itemize}

\paragraph{Generic options}

See help on \href{report/Contents}{generic options} in report objects.

\paragraph{Description}

Figures are top-level report objects and cannot be nested within other
report objects, except \href{report/align}{\texttt{align}}. Figure
objects can have the following types of children:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{report/graph}{\texttt{graph}};
\item
  \href{report/empty}{\texttt{empty}}.
\end{itemize}

\subparagraph{Titles and subtitles}

The input argument \texttt{Caption} can be either a text string, or a
1-by-2 cell array of strings. In the latter case, the first cell will be
printed as a title, and the second cell will be printed as a subtitle.

To split the title or subtitle into multiple lines, use the following
LaTeX commands wrapped in curly brackets:
\texttt{\{\textbackslash{}\textbackslash{}\}} or
\texttt{\{\textbackslash{}\textbackslash{}{[}Xpt{]}\}}, where \texttt{X}
is the width of an extra vertical space (in points) added between the
respective lines.

\subparagraph{Figure handle}

If the option \texttt{'close='} is set to \texttt{false} the figure
window will remain open after the report is published. The handle to
this figure window will be included in the field \texttt{.figureHandle}
of the information struct \texttt{Info} returned by
\href{report/publish}{\texttt{report/publish}}.

\paragraph{Example}


