

    \filetitle{publish}{Compile PDF from report object}{report/publish}

	\paragraph{Syntax}

\begin{verbatim}
[OutpFile,Info] = P.publish(InpFile,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{P} {[} struct {]} - Report object created by the
  \texttt{report.new} function.
\item
  \texttt{InpFile} {[} char {]} - File name under which the compiled PDF
  will be saved.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{OutpFile} {[} char {]} - Name of the resulting PDF.
\item
  \texttt{Info} {[} struct {]} - Information struct with details of
  building the PDF report; see Description.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'abstract='} {[} char \textbar{} \emph{empty} {]} - Abstract
  that will displayed on the title page.
\item
  \texttt{'abstractWidth='} {[} numeric \textbar{} \emph{\texttt{1}} {]}
  - Width of the abstract on the page as a percentage of the full
  default width (between \texttt{0} and \texttt{1}).
\item
  \texttt{'author='} {[} char \textbar{} \emph{empty} {]} - List of
  authors on the title page separated with \texttt{\textbackslash{}and}
  or \texttt{\textbackslash{}\textbackslash{}}.
\item
  \texttt{'cleanup='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Delete all temporary files created when compiling the report.
\item
  \texttt{'compile='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Compile the source files to an actual PDF; if \texttt{false}
  only the source files are created.
\item
  \texttt{'date='} {[} char \textbar{}
  \emph{\texttt{'\textbackslash{}today'}} {]} - Date on the title page.
\item
  \texttt{'display='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Display the \LaTeX compiler report on the final iteration.
\item
  \texttt{'echo='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - If \texttt{true}, the optional flag \texttt{'-echo'} will be
  used in the Matlab function \texttt{system} when compiling the PDF;
  this causes the screen output and all prompts to be displayed for each
  run of the compiler.
\item
  \texttt{'epsToPdf='} {[} char \textbar{} \emph{\texttt{Inf}} {]} -
  Command line arguments for EPSTOPDF; \texttt{Inf} means OS-specific
  arguments are used.
\item
  \texttt{'fontEnc='} {[} char \textbar{} \emph{\texttt{'T1'}} {]} -
  \LaTeX~font encoding.
\item
  \texttt{'makeTitle='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Produce title page (with title, author,
  date, and abstract).
\item
  \texttt{'package='} {[} char \textbar{} cellstr \textbar{}
  \emph{empty} {]} - Package or list of packages that will be imported
  in the preamble of the LaTeX file.
\item
  \texttt{'paperSize='} {[} \texttt{'a4paper'} \textbar{}
  \emph{\texttt{'letterpaper'}} {]} - Paper size.
\item
  \texttt{'orientation='} {[} \emph{\texttt{'landscape'}} \textbar{}
  \texttt{'portrait'} {]} - Paper orientation.
\item
  \texttt{'preamble='} {[} char \textbar{} \emph{empty} {]} -
  \LaTeX~commands that will be placed in the \LaTeX~file preamble.
\item
  \texttt{'timeStamp='} {[} char \textbar{}
  \emph{\texttt{'datestr(now())'}} {]} - String printed in the top-left
  corner of each page.
\item
  \texttt{'tempDir='} {[} char \textbar{} function\_handle \textbar{}
  \emph{\texttt{tempname(pwd())}} {]} - Directory for storing temporary
  files; the directory is deleted at the end of the execution if it's
  empty.
\item
  \texttt{'maxRerun='} {[} numeric \textbar{} \emph{\texttt{5}} {]} -
  Maximum number of times the \LaTeX\\compiler will be run to resolve
  cross-references, etc.
\item
  \texttt{'minRerun='} {[} numeric \textbar{} \emph{\texttt{1}} {]} -
  Minimum number of times the \LaTeX\\compiler will be run to resolve
  cross-references, etc.
\item
  \texttt{'textScale='} {[} numeric \textbar{} \emph{\texttt{0.8}} {]} -
  Percentage of the total page area that will be used; the value can be
  either a scalar (the same percentage for the width and the height) or
  a 1-by-2 vector (the width and the height).
\end{itemize}

\paragraph{Description}

\subparagraph{Difference between \texttt{'display='} and
\texttt{'echo='}}

There are two differences between these otherwise similar options:

\begin{itemize}
\item
  When publishing the final PDF, the PDFLaTeX compiler may be called
  more than once to resolve cross-references, the table of contents, and
  so on. Setting \texttt{'display=' true} only displays the screen
  output from the final iteration only, while \texttt{'echo=' true}
  displays the screen outputs from all iterations.
\item
  In the case of a compiler error unrelated to the \LaTeX~code, the
  compiler may stop and prompt the user to respond. The prompt only
  appears on the screen when \texttt{'echo=' true}. Otherwise, Matlab
  may remain in a busy state with no on-screen information, and
  \texttt{Ctrl+C} may be needed to regain control.
\end{itemize}

\subparagraph{Information struct}

The second output argument, \texttt{Info}, is a struct with details of
building the PDF report. It contains the following fields:

\begin{itemize}
\item
  \texttt{.latexRun} -- the total number of LaTeX compiler runs needed
  to resolve cross-references and other dependencies;
\item
  \texttt{.figureHandle} -- a vector of figure window handles created
  during the report production process, and not closed (i.e.~still
  existing in the Matlab workspace); to keep figure windows open, use
  the figure object option \texttt{'close=' false}. If all
  \texttt{figure} and \texttt{userfigure} objects inside a report have
  \texttt{'close=' true} then \texttt{Info.figureHandle} will be empty.
\item
  \texttt{.tempDir} -- empty unless \texttt{publish} is called with
  \texttt{'cleanup=' false}; in that case, this is the name of a
  temporary directory in which all files are saved necessary to build
  the output PDF are saved.
\item
  \texttt{.tempFile} -- empty unless \texttt{publish} is called with
  \texttt{'cleanup=' false}; in that case, this is the list of all files
  (saved in the temporary directory) necessary to build the output PDF.
\end{itemize}

\paragraph{Example}


