

    \filetitle{series}{Add new data to graph or table}{report/series}

	\paragraph{Syntax}

\begin{verbatim}
P.series(Cap,X,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{P} {[} struct {]} - Report object created by the
  \href{report/new}{\texttt{report.new}} function.
\item
  \texttt{Cap} {[} char \textbar{} cellstr \textbar{} \texttt{@auto} {]}
  - Caption used as a default legend entry in a graph, or in the leading
  column in a table; \texttt{@auto} means that the first comment from
  the input tseries object, \texttt{X}, will be used for the title.
\item
  \texttt{X} {[} tseries {]} - Input data that will be added to the
  current table or graph.
\end{itemize}

\paragraph{Options for both table series and graph
series}

\begin{itemize}
\item
  \texttt{'marks='} {[} cellstr \textbar{} \emph{empty} {]} -
  (Inheritable from parent objects) Marks that will be added to the
  legend entries in graphs, or printed in a third column in tables, to
  distinguish the individual columns of possibly multivariate input
  tseries objects.
\item
  \texttt{'showMarks='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - (Inheritable from parent objects) Use the marks
  defined in the \texttt{'marks='} option to label the individual rows
  when input data is a multivariate tseries object.
\end{itemize}

\paragraph{Options for table series}

\begin{itemize}
\item
  \texttt{'autoData='} {[} function\_handle \textbar{} cell \textbar{}
  \emph{empty} {]} - Function, or a cell array of functions, that will
  be used to produce new columns in the input tseries object (i.e.~new
  rows of ouput in the report).
\item
  \texttt{'condFormat='} {[} struct \textbar{} \emph{empty} {]} -
  (Inheritable from parent objects) Structure with .test and .format
  fields describing conditional formatting of individual table entries.
\item
  \texttt{'decimal='} {[} numeric \textbar{} \emph{\texttt{NaN}} {]} -
  (Inheritable from parent objects) Number of decimals that will be
  displayed; if NaN the \texttt{'format='} option is used instead.
\item
  \texttt{'format='} {[} char \textbar{} \emph{\texttt{'\%.2f'}} {]} -
  (Inheritable from parent objects) Numeric format string; see help on
  the built-in \texttt{sprintf} function.
\item
  \texttt{'footnote='} {[} char \textbar{} \emph{empty} {]} - Footnote
  at the series text.
\item
  \texttt{'highlight='} {[} numeric \textbar{} \emph{empty} {]} -
  Periods for which the data entries will highlighted.
\item
  \texttt{'inf='} {[} char \textbar{}
  \emph{\texttt{'\textbackslash{}ensuremath\{\textbackslash{}infty\}'}}
  {]} - (Inheritable from parent objects) LaTeX string that will be used
  to typeset Inf entries.
\item
  \texttt{'nan='} {[} char \textbar{}
  \emph{\texttt{'\textbackslash{}ensuremath\{\textbackslash{}cdot\}'}}
  {]} - (Inheritable from parent objects) LaTeX string that will be used
  to typeset NaN entries.
\item
  \texttt{'pureZero='} {[} char \textbar{} \emph{empty} {]} -
  (Inheritable from parent objects) LaTeX string that will be used to
  typeset pure zero entries; if empty the zeros will be printed using
  the current numeric format.
\item
  \texttt{'printedZero='} {[} char \textbar{} \emph{empty} {]} -
  (Inheritable from parent objects) LaTeX string that will be used to
  typeset the entries that would appear as zero under the current
  numeric format used; if empty these numbers will be printed using the
  current numeric format.
\item
  \texttt{'rowHighlight='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Highlight the entire row, including the
  text, units and marks at the beginnig; because of a bug in the LaTex
  package \texttt{colortbl}, this option cannot be combined with the
  option \texttt{'highlight='} in
  \href{report/table}{\texttt{report/table}}.
\item
  \texttt{'separator='} {[} char \textbar{} \emph{empty} {]} - LaTeX
  commands that will be inserted immediately after the end of the table
  row, i.e.~appended to \textbackslash{}, within a tabular mode.
\item
  \texttt{'units='} {[} char {]} - (Inheritable from parent objects)
  Description of input data units that will be displayed in the second
  column of tables.
\end{itemize}

\paragraph{Options for graph series}

\begin{itemize}
\item
  \texttt{'legendEntry='} {[} char \textbar{} cellstr \textbar{}
  \texttt{NaN} \textbar{} \emph{\texttt{@auto}} {]} - Legend entries
  used instead of the series caption and marks; \texttt{@auto} means the
  caption and marks will be used to construct legend entries;
  \texttt{NaN} means the series will be exluded from legend.
\item
  \texttt{'plotFunc='} {[} \texttt{@area} \textbar{} \texttt{@bar}
  \textbar{} \texttt{@barcon} \textbar{} \emph{\texttt{@plot}}
  \textbar{} \texttt{@plotcmp} \textbar{} \texttt{@plotpred} \textbar{}
  \texttt{@stem} {]} - (Inheritable from parent objects) Plot function
  that will be used to create graphs.
\item
  \texttt{'plotOptions='} {[} cell \textbar{} \emph{empty} {]} - Options
  passed as the last input arguments to the plot function.
\item
  \texttt{yAxis='} {[} \emph{\texttt{'left'}} \textbar{}
  *\texttt{'right'} {]} - Choose the LHS or RHS axis to plot this
  series; see also comments on LHS-RHS plots in Description.
\end{itemize}

\paragraph{Generic options}

See help on \href{report/Contents}{generic options} in report objects.

\paragraph{Description}

\subparagraph{Using the options \texttt{'nan='}, \texttt{'inf='},
\texttt{'pureZero='} and
\texttt{'printedZero='}}

When specifying the LaTeX string for these options, bear in mind that
the table entries are printed in the math model. This means that
whenever you wish to print a normal text, you need to use an appropriate
text formatting command allowed within a math mode. Most frequently, it
would be \texttt{'\textbackslash{}textnormal\{...\}'}.

\subparagraph{Using the option
\texttt{'plotFunc='}}

When you set the option to \texttt{'plotpred'}, the input data
\texttt{X} (second input argument) must be a multicolumn tseries object
where the first column is the time series observations, and the second
and further columns are its Kalman filter predictions as returned by the
\texttt{filter} function.

\subparagraph{Conditional formatting}

The conditional format struct (or an array of structs) specified through
the \texttt{'condFormat='} option must have two fields, \texttt{.test}
and \texttt{.format}.

The \texttt{.test} field is a text string with a Matlab expression. The
expression must evaluate to a scalar true or false, and can refer to the
following attributes associated with each entry in the data part of the
table:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{value} - the numerical value of the entry,
\item
  \texttt{date} - the date under which the entry appears,
\item
  \texttt{year} - the year under which the entry appears,
\item
  \texttt{period} - the period within the year (e.g.~month or quarter)
  under which the entry appears,
\item
  \texttt{freq} - the frequency of the date under which the entry
  appears,
\item
  \texttt{text} - the text label on the left,
\item
  \texttt{mark} - the text mark on the left used to describe the
  individual rows reported for multivariate series,
\item
  \texttt{row} - the row number within a multivariate series.
\item
  \texttt{rowvalues} - a row vector of all values on the current row.
\end{itemize}

If the table is based on user-defined structure of columns (option
\texttt{'colstruct='} in \href{report/table}{\texttt{table}}), the
following additional attributes are available

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{colname} - descriptor of the column (text in the headline).
\end{itemize}

You can combine a number of attribues within one test, using the logical
operators, e.g.

\begin{verbatim}
'value > 0 && year > 2010'
\end{verbatim}

The \texttt{.format} fields of the conditional format structure consist
of LaTeX commands that will be use to typeset the corresponding entry.
The reference to the entry itself is through a question mark. The
entries are typeset in math mode; this for instance meanse that for bold
or italic typface, you must use the
\texttt{\textbackslash{}mathbf\{...\}} and
\texttt{\textbackslash{}mathit\{...\}} commands.

In addition to standard LaTeX commands, you can use the following
IRIS-specific commands in the format strings:

\begin{itemize}
\item
  \texttt{\textbackslash{}sprintf\{FFFF\}} - to modify the way each
  numeric entry that passes the test is printed by the \texttt{sprintf}
  function; \texttt{FFFF} is one of the standard \texttt{sprintf}
  formatting strings.
\item
  \texttt{\textbackslash{}hide\{?\}} - to hide the actual entry when it
  is supposed to be replaced with something else.
\end{itemize}

You can combine multiple tests and their correponding formats in one
structure; they will be all applied to each entry in the specified
order.

\subparagraph{LHS-RHS plots}

The LHS-RHS report graphs are still an experimental feature.

When the option \texttt{'yAxis='} is used to plot on both the LHS and
the RHS y-axis, the plot functions are restricted to \texttt{@plot},
\texttt{@bar}, \texttt{@area} and \texttt{@stem}. Also, because of a bug
in Matlab, always control the color of the lines, bars and areas in all
LHS-RHS graphs: use either the option \texttt{'plotOptions='} in this
command, or \texttt{'style='} in the respective
\href{report/graph}{\texttt{graph}} command.

\paragraph{Example (Conditional format
structure)}

Typeset negative values in italic, and values in periods before 2010Q1
blue:

\begin{verbatim}
cf = struct();
cf(1).test = 'value < 0';
cf(1).format = '\mathit{?}';
cf(2).test = 'date < qq(2010,1)';
cf(2).format = '\color{blue}';
\end{verbatim}


