

    \filetitle{userfigure}{Insert existing figure window}{report/userfigure}

	\paragraph{Syntax}

\begin{verbatim}
P.userfigure(Caption,H,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{P} {[} struct {]} - Report object created by the
  \href{report/new}{\texttt{report.new}} function.
\item
  \texttt{Caption} {[} char \textbar{} cellstr {]} - Title or a cell
  array with title and subtitle displayed at the top of the figure; see
  Description for splitting the title or subtitle into multiple lines.
\item
  \texttt{H} {[} numeric {]} - Handle to a graphics figure created by
  the user that will be captured and inserted in the report.
\end{itemize}

\paragraph{Options}

See help on \href{report/figure}{\texttt{report/figure}} for options
available.

\paragraph{Generic options}

See help on \href{report/Contents}{generic options} in report objects.

\paragraph{Description}

The function \texttt{report/userfigure} inserts an existing figure
window (created by the user by standard Matlab commands, and referenced
by its handle, \texttt{H}) into a report:

\begin{itemize}
\item
  The figure and the graphs in it must be created \emph{before} you call
  \texttt{report/figure}: any changes or additions to the figure or its
  graphs made after you call the function will not show in the report.
\item
  The userfigure cannot have any children; in other words, you cannot
  call \href{report/graph}{\texttt{report/graph}} after a call to
  \texttt{report/userfigure}.
\end{itemize}

\subparagraph{Titles and subtitles}

The input argument \texttt{Caption} can be either a text string, or a
1-by-2 cell array of strings. In the latter case, the first cell will be
printed as a title, and the second cell will be printed as a subtitle.

To split the title or subtitle into multiple lines, use the following
LaTeX commands wrapped in curly brackets:
\texttt{\{\textbackslash{}\textbackslash{}\}} or
\texttt{\{\textbackslash{}\textbackslash{}{[}Xpt{]}\}}, where \texttt{X}
is the width of an extra vertical space (in points) added between the
respective lines.

\subparagraph{Figure window and figure
handle}

The figure \texttt{H} is saved to a \texttt{fig} file and stored within
the report object. At the time of publishing the report, the figure is
re-created again in a new separate window.

If the option \texttt{'close='} is set to \texttt{false} this new figure
window will remain open after the report is published. The handle to
this figure window will be included in the field \texttt{.figureHandle}
of the information struct \texttt{Info} returned by
\href{report/publish}{\texttt{report/publish}}.

\paragraph{Example}


