
    \foldertitle{sstatelang}{Steady-state file language}{sstatelang/Contents}

	Steady-state (sstate) files are a complementary tool to solve and
 analyse the steady states of more complex models. They allow you to
 create steady-state files independent of the original model files, and
 write the steady-state equations in different ways, manipulate their
 structure or order, split the problem into subblocks, and combine
 numerical and symbolic solutions. Using then the
 \href{sstatelang/Contents}{sstate objects}, you can compile and run
 stand-alone steady-state m-file functions based on your steady-state
 files.
 
 \paragraph{Input parameters}
 
 \begin{itemize}
 \item
   \href{sstatelang/input}{\texttt{!input}} - List of input parameters or
   variables.
 \item
   \href{sstatelang/growthnames}{\texttt{!growthnames}} - Pattern for
   creating growth names.
 \end{itemize}
 
 \paragraph{Equations and assignments}
 
 \begin{itemize}
 \item
   \href{sstatelang/equations}{\texttt{!equations}} - Block of equations
   or assignments.
 \item
   \href{sstatelang/growthnames}{\texttt{!growthnames2imag}} - Pattern
   for creating growth names.
 \item
   \href{sstatelang/solvefor}{\texttt{!solvefor}} - List of variables for
   which the current equations block will be solved.
 \item
   \href{sstatelang/symbolic}{\texttt{!symbolic}} - Attempt to solve the
   current equations block symbolically using the Symbolic Maths Toolbox.
 \end{itemize}
 
 \paragraph{Variables with steady state restricted to be positive}
 
 \begin{itemize}
 \item
   \href{sstatelang/logvariables}{\texttt{!log\_variables}} - Restrict
   the steady state of some of the variables to be positive.
 \item
   \href{sstatelang/allbut}{\texttt{!all\_but}} - Inverse list of
   variables with positive steady states.
 \end{itemize}
 
 \paragraph{Getting on-line help on sstate file language}
 
 \begin{verbatim}
 help sstatelang
 help sstatelang/keyword
 \end{verbatim}



