
    \foldertitle{dates}{Dates and Date Ranges}{dates/Contents}

	\paragraph{Creating IRIS serial date
numbers}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{dates/bb}{\texttt{bb}} - IRIS serial date number for bimonthly
  date.
\item
  \href{dates/bbtoday}{\texttt{bbtoday}} - IRIS serial date number for
  current bi-month.
\item
  \href{dates/hh}{\texttt{hh}} - IRIS serial date number for half-yearly
  date.
\item
  \href{dates/hhtoday}{\texttt{hhtoday}} - IRIS serial date number for
  current half-year.
\item
  \href{dates/mm}{\texttt{mm}} - IRIS serial date number for monthly
  date.
\item
  \href{dates/mmtoday}{\texttt{mmtoday}} - IRIS serial date number for
  current month.
\item
  \href{dates/qq}{\texttt{qq}} - IRIS serial date number for quarterly
  date.
\item
  \href{dates/qqtoday}{\texttt{qqtoday}} - IRIS serial date number for
  current quarter.
\item
  \href{dates/ww}{\texttt{ww}} - IRIS serial date number for weekly
  date.
\item
  \href{dates/wwtoday}{\texttt{wwtoday}} - IRIS serial date number for
  current week.
\item
  \href{dates/yy}{\texttt{yy}} - IRIS serial date number for yearly
  date.
\item
  \href{dates/yytoday}{\texttt{yytoday}} - IRIS serial date number for
  current year.
\end{itemize}

\paragraph{Computing special dates (daily dates
only)}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{dates/datbom}{\texttt{datbom}} - Beginning of month for the
  specified daily date.
\item
  \href{dates/datboq}{\texttt{datboq}} - Beginning of quarter for the
  specified daily date.
\item
  \href{dates/datboy}{\texttt{datboy}} - Beginning of year for the
  specified daily date.
\item
  \href{dates/dateom}{\texttt{dateom}} - End of month for the specified
  daily date.
\item
  \href{dates/dateoq}{\texttt{dateoq}} - End of quarter for the
  specified daily date.
\item
  \href{dates/dateoy}{\texttt{dateoy}} - End of year for the specified
  daily date.
\end{itemize}

\paragraph{Creating date ranges}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{dates/datrange}{\texttt{datrange}} - Numerically safe way to
  create a date range.
\item
  \href{dates/dat2ttrend}{\texttt{dat2ttrend}} - Construct linear time
  trend from date range.
\item
  \href{dates/datxtick}{\texttt{datxtick}} - Change ticks, labels and/or
  date frequency on x-axis in existing tseries graphs.
\end{itemize}

\paragraph{Converting dates}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{dates/clp2dat}{\texttt{clp2dat}} - Convert text in system
  clipboard to dates.
\item
  \href{dates/dat2char}{\texttt{dat2char}} - Convert dates to character
  array.
\item
  \href{dates/dat2charlist}{\texttt{dat2charlist}} - Convert dates to a
  comma-separated list.
\item
  \href{dates/dat2clp}{\texttt{dat2clp}} - Convert dates to text and
  paste to system clipboard.
\item
  \href{dates/dat2dec}{\texttt{dat2dec}} - Convert dates to decimal
  grid.
\item
  \href{dates/dat2str}{\texttt{dat2str}} - Convert IRIS dates to cell
  array of strings.
\item
  \href{dates/dat2ypf}{\texttt{dat2ypf}} - Convert IRIS serial date
  number to year, period and frequency.
\item
  \href{dates/dec2dat}{\texttt{dec2dat}} - Convert decimal
  representation of date to IRIS serial date number.
\item
  \href{dates/str2dat}{\texttt{str2dat}} - Convert strings to IRIS
  serial date numbers.
\end{itemize}

\paragraph{Date comparison}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{dates/datcmp}{\texttt{datcmp}} - Compare two IRIS serial date
  numbers.
\item
  \href{dates/datdiff}{\texttt{datdiff}} - Number of periods between two
  dates with check for date frequency.
\item
  \href{dates/rngcmp}{\texttt{rngcmp}} - Compare two IRIS date ranges.
\end{itemize}

\paragraph{Daily and weekly dates}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{dates/daysinyear}{\texttt{daysinyear}} - Number of days in year.
\item
  \href{dates/dd}{\texttt{dd}} - Matlab serial date numbers that can be
  used to construct daily tseries objects.
\item
  \href{dates/ddtoday}{\texttt{ddtoday}} - Matlab serial date number for
  today's date.
\item
  \href{dates/ww2day}{\texttt{ww2day}} - Convert weekly IRIS serial date
  number to Matlab serial date number.
\item
  \href{dates/weeksinyear}{\texttt{weeksinyear}} - Number of weeks in
  year.
\end{itemize}

\paragraph{Getting on-line help on date
functions}

\begin{verbatim}
help dates
help dates/function_name
\end{verbatim}



