

    \filetitle{qplot}{Quick report}{qreport/qplot}

	\paragraph{Syntax}

\begin{verbatim}
[FF,AA,PDb] = qplot(QFile,D,Range,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{QFile} {[} char {]} - Name of the q-file that defines the
  contents of the individual graphs.
\item
  \texttt{D} {[} struct {]} - Database with input data.
\item
  \texttt{Range} {[} numeric {]} - Date range.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{FF} {[} numeric {]} - Handles to figures created by
  \texttt{qplot}.
\item
  \texttt{AA} {[} cell {]} - Handles to axes created by \texttt{qplot}.
\item
  \texttt{PDb} {[} struct {]} - Database with actually plotted series.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'addClick='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Make axes expand in a new graphics figure upon
  mouse click.
\item
  \texttt{'caption='} {[} cellstr \textbar{} @comment \textbar{} *empty*
  {]} - Strings that will be used for titles in the graphs that have no
  title in the q-file.
\item
  \texttt{'clear='} {[} numeric \textbar{} \emph{empty} {]} - Serial
  numbers of graphs (axes objects) that will not be displayed.
\item
  \texttt{'dbSave='} {[} cellstr \textbar{} \emph{empty} {]} - Options
  passed to \texttt{dbsave} when \texttt{'saveAs='} is used.
\item
  \texttt{'drawNow='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Call Matlab \texttt{drawnow} function upon completion of all
  figures.
\item
  \texttt{'grid='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Add grid lines to all graphs.
\item
  \texttt{'highlight='} {[} numeric \textbar{} cell \textbar{}
  \emph{empty} {]} - Date range or ranges that will be highlighted.
\item
  \texttt{'interpreter='} {[} \emph{\texttt{'latex'}} \textbar{} `none'
  {]} - Interpreter used in graph titles.
\item
  \texttt{'mark='} {[} cellstr \textbar{} \emph{empty} {]} - Marks that
  will be added to each legend entry to distinguish individual columns
  of multivariated tseries objects plotted.
\item
  \texttt{'overflow='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Open automatically a new figure window if
  the number of subplots exceeds the available total;
  \texttt{'overflow' = false} means an error will occur instead.
\item
  \texttt{'prefix='} {[} char \textbar{} \emph{\texttt{'P\%g\_'}} {]} -
  Prefix (a \texttt{sprintf} format string) that will be used to precede
  the name of each entry in the \texttt{PDb} database.
\item
  \texttt{'round='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
  Round the input data to this number of decimals before plotting.
\item
  \texttt{'saveAs='} {[} char \textbar{} \emph{empty} {]} - File name
  under which the plotted data will be saved either in a CSV data file
  or a PS graphics file; you can use the \texttt{'dbsave='} option to
  control the options used when saving CSV.
\item
  \texttt{'style='} {[} struct \textbar{} \emph{empty} {]} - Style
  structure that will be applied to all figures and their children
  created by the \texttt{qplot} function.
\item
  \texttt{'subplot='} {[} \emph{`auto'} \textbar{} numeric {]} - Default
  subplot division of figures, can be modified in the q-file.
\item
  \texttt{'sstate='} {[} struct \textbar{} model \textbar{} \emph{empty}
  {]} - Database or model object from which the steady-state values
  referenced to in the quick-report file will be taken.
\item
  \texttt{'style='} {[} struct \textbar{} \emph{empty} {]} - Style
  structure that will be applied to all created figures upon completion.
\item
  \texttt{'transform='} {[} function\_handle \textbar{} \emph{empty} {]}
  - Function that will be used to trans
\item
  \texttt{'tight='} {[} \texttt{true} \textbar{} \emph{\texttt{false}}
  {]} - Make the y-axis in each graph tight.
\item
  \texttt{'vLine='} {[} numeric \textbar{} \emph{empty} {]} - Dates at
  which vertical lines will be plotted.
\item
  \texttt{'zeroLine='} {[} \texttt{true} \textbar{}
  \emph{\texttt{false}} {]} - Add a horizontal zero line to graphs whose
  y-axis includes zero.
\end{itemize}

\paragraph{Description}

\paragraph{Example}


