
    \foldertitle{grfun}{Graphics Functions (grfun Package)}{grfun/Contents}

	\paragraph{Graphics functions}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{grfun/bottomlegend}{\texttt{bottomlegend}} - Horizontal graph
  legend displayed at the bottom of the figure window.
\item
  \href{grfun/ftitle}{\texttt{ftitle}} - Add title to figure window.
\item
  \href{grfun/highlight}{\texttt{highlight}} - Highlight specified range
  or date range in a graph.
\item
  \href{grfun/hline}{\texttt{hline}} - Add horizontal line with text
  caption at the specified position.
\item
  \href{grfun/maxfigure}{\texttt{maxfigure}} - Maximize figure window.
\item
  \href{grfun/movetobkg}{\texttt{movetobkg}} - Move graphics objects to
  the background.
\item
  \href{grfun/movetosubplot}{\texttt{movetosubplot}} - Move an existing
  axes object or legend to specified subplot position.
\item
  \href{grfun/plotcircle}{\texttt{plotcircle}} - Draw a circle or disc.
\item
  \href{grfun/plotpp}{\texttt{plotpp}} - Plot prior and/or posterior
  distributions and/or posterior mode.
\item
  \href{grfun/plotmat}{\texttt{plotmat}} - Visualise 2D matrix.
\item
  \href{grfun/plotneigh}{\texttt{plotneigh}} - Plot local behaviour of
  objective function after estimation.
\item
  \href{grfun/vline}{\texttt{vline}} - Add vertical line with text
  caption at the specified position.
\item
  \href{grfun/zeroline}{\texttt{zeroline}} - Add zero line if Y-axis
  limits include zero.
\end{itemize}

\paragraph{Getting on-line help on qreport
functions}

\begin{verbatim}
help grfun
help grfun/function_name
\end{verbatim}



