

    \filetitle{plotpp}{Plot prior and/or posterior distributions and/or posterior mode}{grfun/plotpp}

	\paragraph{Syntax}

\begin{verbatim}
[PrG,PoG,H] = grfun.plotpp(E,[],[],...)
[PrG,PoG,H] = grfun.plotpp(E,Est,[],...)
[PrG,PoG,H] = grfun.plotpp(E,[],Theta,...)
[PrG,PoG,H] = grfun.plotpp(E,[],Stats,...)
[PrG,PoG,H] = grfun.plotpp(E,Est,Theta,...)
[PrG,PoG,H] = grfun.plotpp(E,Est,Stats,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{E} {[} struct {]} - Estimation input struct, see
  \href{model/estimate}{\texttt{estimate}}, with prior function handles
  from the \href{logdist/Contents}{logdist} package.
\item
  \texttt{Est} {[} struct \textbar{} empty {]} - Output struct returned
  by the \href{model/estimate}{\texttt{model/estimate}} function;
  \texttt{Est} will be used to plot the maximised posterior modes.
\item
  \texttt{Theta} {[} numeric \textbar{} empty {]} - Array with the chain
  of draws from the posterior simulator
  \href{poster/arwm}{\texttt{arwm}}.
\item
  \texttt{Stats} {[} struct \textbar{} empty {]} - Output struct
  returned by the posterior simulator statistics function
  \href{poster/stats}{\texttt{stats}}.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{PrG} {[} struct {]} - Struct with x- and y-axis coordinates to
  plot the prior distribution for each parameter.
\item
  \texttt{PoG} {[} struct {]} - Struct with x- and y-axis coordinates to
  plot the posterior distribution for each parameter.
\item
  \texttt{H} {[} struct {]} - Struct with handles to the graphics
  objects plotted by \texttt{plotpp}; the struct has the following
  fields with vectors of handles: \texttt{figure}, \texttt{axes},
  \texttt{prior}, \texttt{poster}, \texttt{bounds}, \texttt{init},
  \texttt{mode}, \texttt{title}.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'caption='} {[} \emph{empty} \textbar{} cellstr {]} -
  User-supplied graph titles; if empty, default captions will be
  automatically created.
\item
  \texttt{'describe='} {[} \emph{`auto'} \textbar{} true \textbar{}
  false {]} - Include information on prior distributions, starting
  values, and maximised posterior modes in the graph titles;
  \texttt{'auto'} means the descriptions will be shown only if
  \texttt{'plotPrior='} is true.
\item
  \texttt{'ksdensity='} {[} numeric \textbar{} \emph{empty} {]} - Number
  of points over which the density will be calculated; if empty, default
  number will be used depending on the backend function available.
\item
  \texttt{'plotInit='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} \textbar{} cell {]} - Plot starting values (initial
  consition used in posterior mode maximisation) as vertical stems.
\item
  \texttt{'plotPrior='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} \textbar{} cell {]} - Plot prior distributions.
\item
  \texttt{'plotMode='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} \textbar{} cell {]} - Plot maximised posterior modes as
  vertical stems; the modes are taken from \texttt{Est} (and not from
  \texttt{Stats} or \texttt{Theta}).
\item
  \texttt{'plotPoster='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} \textbar{} cell {]} - Plot posterior distributions.
\item
  \texttt{'plotBounds='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} \textbar{} cell {]} - Plot lower and/or upper bounds as
  vertical lines; if \texttt{false}, the bounds will be plotted only
  added if within the graph x-limits.
\item
  \texttt{'sigma='} {[} numeric \textbar{} \emph{3} {]} - Number of std
  devs from the mean or the mode (whichever covers a larger area) to the
  left and to right that will be plotted unless running out of bounds.
\item
  \texttt{'tight='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  {]} - Make graph axes tight.
\item
  \texttt{'title=}' {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  \textbar{} cell {]} - Display graph titles, and specify graphics
  options for the titles.
\item
  \texttt{'xLims='} {[} struct \textbar{} \emph{empty} {]} - Control the
  x-limits of the prior and posterior graphs.
\end{itemize}

\paragraph{Description}

The options that control what will be plotted in the graphs (i.e.
\texttt{'plotInit='}, \texttt{'plotPrior='}, \texttt{'plotMode='},
\texttt{'plotPoster='}, \texttt{'plotBounds='},\texttt{'title='}) can be
set to one of the following three values:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{true},
\item
  \texttt{false},
\item
  a cell array with sub-options to control the appearance of the
  respetive line; these will be passed into the respective plotting
  function.
\end{itemize}

\paragraph{Example}


