

    \filetitle{vline}{Add vertical line with text caption at the specified position}{grfun/vline}

	\paragraph{Syntax}

\begin{verbatim}
[Ln,Cp] = grfun.vline(Xpos,...)
[Ln,Cp] = grfun.vline(Ax,XPos,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{'XPos}' {[} numeric {]} - Horizontal position or vector of
  positions at which the vertical line or lines will be drawn.
\item
  \texttt{Ax} {[} numeric {]} - Handle to an axes object (graph) or to a
  figure window in which the the line will be added; if not specified
  the line will be added to the current axes.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{Ln} {[} numeric {]} - Handle to the vline(s) plotted (line
  objects).
\item
  \texttt{Cp} {[} numeric {]} - Handle to the caption(s) created (text
  objects).
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'caption='} {[} char {]} - Annotate vline with a text string.
\item
  \texttt{'excludeFromLegend='} {[} \emph{\texttt{true}} \textbar{}
  \texttt{false} {]} - Exclude vline from legend.
\item
  \texttt{'hPosition='} {[} \texttt{'center'} \textbar{} \texttt{'left'}
  \textbar{} \emph{\texttt{'right'}} {]} - Horizontal position of the
  caption.
\item
  \texttt{'vPosition='} {[} \texttt{'bottom'} \textbar{}
  \texttt{'middle'} \textbar{} \emph{\texttt{'top'}} \textbar{} numeric
  {]} - Vertical position of the caption.
\item
  \texttt{'timePosition='} {[} \texttt{'after'} \textbar{}
  \texttt{'before'} \textbar{} \emph{\texttt{'middle'}} {]} - Placement
  of the vertical line on the time axis: in the middle of the specified
  period, immediately before it (between the specified period and the
  previous one), or immediately after it (between the specified period
  and the next one).
\end{itemize}

\paragraph{Description}

\paragraph{Example}


