

    \filetitle{irisget}{Query current IRIS config options}{config/irisget}

	\paragraph{Syntax}

\begin{verbatim}
Value = irisget(Option)
S = irisget()
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{Option} {[} char {]} - Name of the queried IRIS configuration
  option.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{Value} {[} \ldots{} {]} - Current value of the queried
  configuration option.
\item
  \texttt{S} {[} struct {]} - Structure with all configuration options
  and their current values.
\end{itemize}

\paragraph{Description}

You can view any of the modifiable options listed in
\href{config/irisset}{\texttt{irisset}}, plus the following
non-modifiable ones (these cannot be changed by the user):

\begin{itemize}
\item
  \texttt{'userConfigPath='} {[} char {]} - The path to the user
  configuration file called by the last executed
  \href{config/irisstartup}{\texttt{irisstartup}}.
\item
  \texttt{'irisRoot='} {[} char {]} - The current IRIS root directory.
\item
  \texttt{'version='} {[} char {]} - The current IRIS version string.
\end{itemize}

When called without any input arguments, the \texttt{irisget} function
returns a struct with all options and their current values.

When used as input arguments in the \texttt{irisget} function, the
option names are case-insensitive. When referring to field names of an
output struct returned by the \texttt{irisget} function, all option
names are lower-case and case-sensitive.

\paragraph{Example}

\begin{verbatim}
irisget('dateFormat')
ans =
YFP

g = irisget();
g.dateformat
ans =
YFP
\end{verbatim}


