

    \filetitle{estimate}{Estimate FAVAR using static principal components}{FAVAR/estimate}

	\paragraph{Syntax}

\begin{verbatim}
[A,D,CC,F,U,E,CTF] = estimate(A,D,Range,[R,Q],...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{A} {[} FAVAR {]} - Empty FAVAR object.
\item
  \texttt{D} {[} struct {]} - Input database.
\item
  \texttt{Range} {[} numeric {]} - Estimation range.
\item
  \texttt{R} {[} numeric {]} - Selection criterion for the number of
  factors: Minimum requested proportion of input data volatility
  explained by the factors.
\item
  \texttt{Q} {[} numeric {]} - Selection criterion for the number of
  factors: Maximum number of factors.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\item
  \texttt{A} {[} FAVAR {]} - Estimated FAVAR object.
\item
  \texttt{D} {[} struct {]} - Output database.
\item
  \texttt{CC} {[} tseries {]} - Estimates of common components in the
  FAVAR observables.
\item
  \texttt{F} {[} tseries {]} - Estimates of factors.
\item
  \texttt{U} {[} struct \textbar{} tseries {]} - Idiosyncratic
  residuals.
\item
  \texttt{E} {[} tseries {]} - Factor VAR residuals.
\item
  \texttt{CTF} {[} tseries {]} - Contributions of individual input
  series to the estimated factors.
\end{itemize}

\paragraph{Options}

\begin{itemize}
\item
  \texttt{'cross='} {[} \emph{\texttt{true}} \textbar{} \texttt{false}
  \textbar{} numeric {]} - Keep off-diagonal elements in the covariance
  matrix of idiosyncratic residuals; if false all cross-covariances are
  reset to zero; if a number between zero and one, all cross-covariances
  are multiplied by that number.
\item
  \texttt{'order='} {[} numeric \textbar{} \emph{1} {]} - Order of the
  VAR for factors.
\item
  \texttt{'output='} {[} \emph{\texttt{'auto'}} \textbar{}
  \texttt{'dbase'} \textbar{} \texttt{'tseries'} {]} - Format of output
  data.
\item
  \texttt{'rank='} {[} numeric \textbar{} \emph{\texttt{Inf}} {]} -
  Restriction on the rank of the factor VAR residuals.
\end{itemize}

\paragraph{Description}

\paragraph{Example}


