

    \filetitle{get}{Query model object properties}{FAVAR/get}

	\paragraph{Syntax}

\begin{verbatim}
Ans = get(A,Query)
[Ans,Ans,...] = get(A,Query,Query,...)
\end{verbatim}

\paragraph{Input arguments}

\begin{itemize}
\item
  \texttt{A} {[} FAVAR {]} - FAVAR object.
\item
  \texttt{Query} {[} char {]} - Query to the FAVAR object.
\end{itemize}

\paragraph{Output arguments}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{Ans} {[} \ldots{} {]} - Answer to the query.
\end{itemize}

\paragraph{Valid queries to FAVAR
objects}

\subparagraph{System matrices}

\begin{itemize}
\item
  \texttt{'A*'} Returns {[} numeric {]} the transition matrix of the
  underlying VAR system on factors.
\item
  \texttt{'B'} Returns {[} numeric {]} tne matrix mapping the impact of
  structural residuals on the factors in the underlying VAR.
\item
  \texttt{'C'} Returns {[} numeric {]} the matrix mapping the factors
  into the observables.
\item
  \texttt{'Omega'} Returns {[} numeric {]} the reduced-form covariance
  matrix of the residuals in the underlying VAR.
\item
  \texttt{'Sigma'} Returns {[} numeric {]} the covariance matrix of
  idiosyncratic shocks.
\end{itemize}

\subparagraph{Underlying VAR}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{'VAR'} Returns {[} VAR {]} a VAR object describing the factor
  dynamics.
\end{itemize}

\subparagraph{Eigenvalues and singular
values}

\begin{itemize}
\item
  \texttt{'eig'} Returns {[} numeric {]} the vector of eigenvalues of
  the underlying VAR.
\item
  \texttt{'sing'} Returns {[} numeric {]} the vector of singular values
  from the principal component estimation step.
\end{itemize}

\subparagraph{Observables and factors}

\begin{itemize}
\item
  \texttt{'mean'} Returns {[} numeric {]} the estimated mean of the
  observables used to standardise the input data.
\item
  \texttt{'std'} Returns {[} numeric {]} the estimated std deviations of
  the observables used to standardise the input data.
\item
  \texttt{'ny'} Returns {[} numeric {]} the number of observables.
\item
  \texttt{'nx'} Returns {[} numeric {]} the number of factors.
\item
  \texttt{'yList'} Returns {[} cellstr {]} the list of the names of
  observables.
\end{itemize}

\paragraph{Description}

\paragraph{Example}


