
    \foldertitle{logdist}{Probability Distributions (logdist Package)}{logdist/Contents}

	The logdist package gives quick access to basic univariate
distributions, and in particular to functions proportional to the
logarithm of those basic distributions. Its primary use is setting up
priors in the \href{model/estimate}{\texttt{model/estimate}} and
\href{poster/arwm}{\texttt{poster/arwm}} functions.

The logdist package is called to create function handles that have
several different modes of use. The primary use is to compute values
that are proportional to the log of the respective density. In addition,
the function handles also give you access to extra information (such as
the the proper p.d.f., the name, mean, std dev, mode, and stuctural
parameters of the distribution), and to a random number generator from
the respective distribution.

Logdist methods:

\paragraph{Getting function handles for univariate
distributions}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{logdist/chisquare}{\texttt{chisquare}} - Create function
  proportional to log of Chi-Squared distribution.
\item
  \href{logdist/normal}{\texttt{normal}} - Create function proportional
  to log of Normal distribution.
\item
  \href{logdist/lognormal}{\texttt{lognormal}} - Create function
  proportional to log of log-normal distribution.
\item
  \href{logdist/beta}{\texttt{beta}} - Create function proportional to
  log of beta distribution.
\item
  \href{logdist/gamma}{\texttt{gamma}} - Create function proportional to
  log of gamma distribution.
\item
  \href{logdist/invgamma}{\texttt{invgamma}} - Create function
  proportional to log of inv-gamma distribution.
\item
  \href{logdist/t}{\texttt{t}} - Create function proportional to log of
  Student T distribution.
\item
  \href{logdist/uniform}{\texttt{uniform}} - Create function
  proportional to log of uniform distribution.
\end{itemize}

\paragraph{Calling the logdist function
handles}

The function handles \texttt{F} created by the logdist package functions
can be called the following ways:

\begin{itemize}
\item
  Get a value proportional to the log-density of the respective
  distribution at a particular point; this call is used within the
  \href{poster/Contents}{posterior simulator}:

  y = F(x)
\item
  Get the density of the respective distribution at a particular point:

  y = F(x,`pdf')
\item
  Get the characteristics of the distribution -- mean, std deviation,
  mode, and information (the inverse of the second derivative of the log
  density):

  m = F({[}{]},`mean') s = F({[}{]},`std') o = F({[}{]},`mode') i =
  F({[}{]},`info')
\item
  Get the underlying ``structural'' parameters of the respective
  distribution:

  a = F({[}{]},`a') b = F({[}{]},`b')
\item
  Get the name of the distribution (the names correspond to the function
  names, i.e.~can be either of \texttt{'normal'}, \texttt{'lognormal'},
  \texttt{'beta'}, \texttt{'gamma'}, \texttt{'invgamma'},
  \texttt{'uniform'}):

  name = F({[}{]},`name')
\item
  Draw a vector or matrix of random numbers from the distribution;
  drawing from beta, gamma, and inverse gamma requires the Statistics
  Toolbox:

  a = F({[}{]},`draw',1,1000);

  size(a) ans = 1 10000
\end{itemize}

\paragraph{Getting on-line help on logdist
functions}

\begin{verbatim}
help logdist
help logdist/function_name
\end{verbatim}



